### 2024-02-12 manuscript.qmd
add work in progress analysis

---
title: "Replication of Gantman et al. 2024"
author: "219 2024"
format: html
---

```{r}
#| Libraries
#| include: false

library(readr)
library(dplyr)
library(jsonlite)
library(ggplot2)
```

```{r}
#| Download the data from the OSF

```

```{r}
#| label: Load the behavioral data
#| include: false

behavioral_data <- read_csv('data/final/behavioral.csv')
```

```{r}
#| label: Filter out the subjects who got fashion words twice due to programming error
#| include: false

exclude_for_fashion_twice_subjects <- behavioral_data %>%
  filter(phase == "fashion", task == "response") %>%
  group_by(subject_id) %>%
  count() %>%
  filter(n == 600) %>%
  pull(subject_id)
```

```{r}
#| label: Get subject non-response rate
#| include: false

subject_non_response_rate <- behavioral_data %>%
  filter(phase == "moral" | phase == "fashion") %>%
  filter(task == "response") %>%
  group_by(subject_id) %>%
  summarise(non_response_rate = mean(is.na(rt)))

exclude_for_non_response_subjects <- subject_non_response_rate %>%
  filter(non_response_rate > 0.5) %>%
  pull(subject_id)
```

```{r}
#| label: Compute subject non-word response rate
#| include: false

subject_non_word_response_rate <- behavioral_data %>%
  filter(phase == "moral" | phase == "fashion") %>%
  filter(task == "response") %>%
  group_by(subject_id) %>%
  mutate(non_word_response = ifelse(
    (is_word == FALSE & correct == TRUE) |
    (is_word == TRUE & correct == FALSE), 1, 0)) %>%
  summarize(non_word_response_rate = mean(non_word_response))

exclude_for_non_word_response_subjects <- subject_non_word_response_rate %>%
  filter(non_word_response_rate > 0.9) %>%
  pull(subject_id)
```

```{r}
#| label: Create filtered data set by applying exclusions
#| include: false

exlcuded_subjects <- c(exclude_for_fashion_twice_subjects, exclude_for_non_response_subjects, exclude_for_non_word_response_subjects)

behavioral_data_filtered <- behavioral_data %>%
  filter(!subject_id %in% exlcuded_subjects)
```

```{r}
#| label: Select relevant test data
#| include: false

behavioral_data_test_set <- behavioral_data_filtered %>%
  filter(phase == "moral" | phase == "fashion") %>%
  filter(task == "response") %>%
  select(subject_id, word_type, is_word, correct, rt) %>%
  mutate(word_category = ifelse(word_type %in% c("fashion", "moral"), "category", "non-category"),
         category = ifelse(word_type %in% c("fashion", "non-fashion"), "fashion", "moral"))
```

```{r}
#| Check accuracy
#| include: false

subject_level_accuracy <- behavioral_data_test_set %>%
  group_by(subject_id, word_category, category, is_word) %>%
  summarise(accuracy = mean(correct))
```

```{r}
#| label: Behavioral pop-out effect

behavioral_pop_out_data <- subject_level_accuracy %>%
  filter(is_word == TRUE)

ggplot(behavioral_pop_out_data, aes(x=word_category, y=accuracy, group=subject_id))+
  geom_point()+
  geom_line()+
  #labs(x="Word Type", y="Accuracy")+
  facet_grid(.~category)+
  theme_bw()
```

```{r}
#| Load eeg data
#| include: false

eeg_data <- read_csv("data/final/eeg.csv") %>%
  filter(!subject %in% excluded_subjects)
```

```{r}
#| label: Subject ERPs
#| include: false

subject_eeg <- eeg_data %>%
  filter(good_segment == TRUE) %>%
  filter(electrode %in% c("Cz", "Pz")) %>%
  filter(correct == TRUE) %>%
  group_by(subject, t, electrode, word_type, is_word) %>%
  summarize(v = mean(v)) %>%
  mutate(word_category = ifelse(word_type %in% c("fashion", "moral"), "category", "non-category"),
         category = ifelse(word_type %in% c("fashion", "non-fashion"), "fashion", "moral"))
```

```{r}
grand_average <- subject_eeg %>%
  group_by(t, electrode, word_category, category, is_word) %>%
  summarize(M = mean(v), SE = sd(v)/sqrt(n()))
```

```{r}
ggplot(grand_average, aes(x=t, y=M, color=is_word, linetype=word_category)) +
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = 0)+
  geom_ribbon(aes(ymin=M-SE, ymax=M+SE, fill=is_word), alpha=0.2, color=NA)+
  geom_line()+
  scale_x_continuous(breaks=c(0,500, 1000))+
  facet_grid(electrode~category)+
  labs(x="Time since word onset (ms)", y="Voltage (uV)", color="Is word?", fill="Is word?", linetype="Word Category")+
  theme_minimal()+
  theme(panel.grid = element_blank())
```

```{r}
count_good_trials <- eeg_data %>%
  dplyr::filter(good_segment == TRUE) %>%
  dplyr::filter(electrode %in% c("Cz", "Pz")) %>%
  group_by(subject, electrode, word_type, is_word, event_id) %>%
  slice(1) %>%
  group_by(subject, electrode, word_type, is_word) %>%
  summarize(n = n())

count_good_trials
```

### 2024-02-14 manuscript.qmd
typo fix

@@
 
-exlcuded_subjects <- c(exclude_for_fashion_twice_subjects, exclude_for_non_response_subjects, exclude_for_non_word_response_subjects)
+excluded_subjects <- c(exclude_for_fashion_twice_subjects, exclude_for_non_response_subjects, exclude_for_non_word_response_subjects)
 
 behavioral_data_filtered <- behavioral_data %>%
-  filter(!subject_id %in% exlcuded_subjects)
+  filter(!subject_id %in% excluded_subjects)
 ```

### 2024-02-14 preprocessing/run_preprocessing_local_machine.R

@@ -2,7 +2,8 @@ library(readr)
 library(stringr)
 source("preprocessing/preprocessing-eeg-functions.R")
 
-subjects <- c("01", "02", "03", "04", "05", "06", "07", "08", "09", "10", "11", "12", "13", "14")
+subjects <- c("01", "02", "03", "04", "05", "06", "07", "08", "09", "10", "11", "12", "13", "14",
+              "16", "17", "18", "20")
 
 for(subject in subjects){
   

### 2024-02-20 manuscript.qmd
updating analysis

@@
   pull(subject_id)
+```
+
+```{r}
+#| label: Flip responses for subject 01
+#| include: false
+
+behavioral_data <- behavioral_data %>%
+  mutate(correct = ifelse(subject_id == "01", !correct, correct))
 ```
@@
 ```{r}
+#| label: model the GEE
+
+library(gee)
+
+m <- gee(correct ~ word_category,
+    id = subject_id,
+    subset = is_word == TRUE & category == "moral",
+    data = behavioral_data_test_set,
+    family = binomial,
+    corstr = "exchangeable")
+
+summary(m)
+```
+
+```{r}
 #| Load eeg data
@@
   filter(!subject %in% excluded_subjects)
+```
+
+```{r}
+#| label: Flip subject 01s responses
+#| include: false
+
+eeg_data <- eeg_data %>%
+  mutate(correct = ifelse(subject == "01", !correct, correct))
 ```
@@
   group_by(subject, t, electrode, word_type, is_word) %>%
-  summarize(v = mean(v)) %>%
+  summarize(v = mean(v), n=n()) %>%
   mutate(word_category = ifelse(word_type %in% c("fashion", "moral"), "category", "non-category"),
@@
   group_by(t, electrode, word_category, category, is_word) %>%
-  summarize(M = mean(v), SE = sd(v)/sqrt(n()))
+  summarize(M = weighted.mean(v, n), SE = sd(v)/sqrt(n()))
 ```

### 2024-02-20 preprocessing/extract-events.R

@@ -2,9 +2,10 @@ library(edfReader)
 library(purrr)
 library(dplyr)
 library(jsonlite)
+library(fuzzyjoin)
 
-eeg.file <- "data/raw/eeg/subject-08-eeg_2024-02-10.bdf"
-beh.file <- "data/raw/beh/219_2024_behavioral_08.json"
+eeg.file <- "data/raw/eeg/subject-25-eeg_2024-02-14.bdf"
+beh.file <- "data/raw/beh/219_2024_behavioral_25.json"
 
 extract_events <- function(eeg.file, beh.file){
   
@@ -21,7 +22,9 @@ extract_events <- function(eeg.file, beh.file){
   trials <- behavioral.data %>% 
     dplyr::filter(task=="response") %>% 
     dplyr::filter(phase!="practice") %>%
-    select(word_type, is_word, correct) %>%
+    select(word_type, is_word, correct, time_elapsed) %>%
+    mutate(time_since_first_trial = (time_elapsed - min(time_elapsed))/1000) %>%
+    select(-time_elapsed) %>%
     mutate(row_id = 1:n())
   
   ## extract EEG events
@@ -57,14 +60,15 @@ extract_events <- function(eeg.file, beh.file){
   # indicating that the experimenter dragged the window 
   # under the sensor after starting recording
   
-  if(filtered.events$time[2] - filtered.events$time[1] > 10){
+  while(filtered.events$time[2] - filtered.events$time[1] > 10){
     # remove the first row
     filtered.events <- filtered.events %>%
       slice(-1) %>%
       mutate(row_id = 1:n())
   }
   
-  while(nrow(filtered.events) > 600){
+  removed_one <- TRUE
+  while(removed_one){
     # remove the first row where diff is less than 1.9
     fake.event <- filtered.events %>% 
      mutate(diff = time - lag(time)) %>%
@@ -73,19 +77,32 @@ extract_events <- function(eeg.file, beh.file){
       pull(sample_id)
     
     if(length(fake.event) == 0){
-      
-      break
+      removed_one <- FALSE
     }
     
     filtered.events <- filtered.events %>%
       dplyr::filter(!sample_id %in% fake.event) %>%
       mutate(row_id = 1:n())
   }
- 
-  final_events <- filtered.events %>% 
-    left_join(trials, by="row_id") %>%
+  
+  # add a check that compares time of the event to the time in the behavioral
+  # data file to align the two datasets when there are fewer events recorded
[…]

### 2024-02-20 preprocessing/mege-local.R

@@ -6,6 +6,8 @@ library(dplyr)
 files <- list.files("data/preprocessed", pattern = "*.csv", full.names = TRUE)
 data <- lapply(files, function(x){
   read_csv(x, col_types = "cdcllcddddllc")
-}) %>% bind_rows()
+}) %>% 
+  bind_rows() %>% 
+  dplyr::filter(electrode %in% c("Cz", "Pz"))
 
 write_csv(data, "data/final/eeg.csv")

### 2024-02-20 preprocessing/run_preprocessing_local_machine.R

@@ -2,8 +2,9 @@ library(readr)
 library(stringr)
 source("preprocessing/preprocessing-eeg-functions.R")
 
-subjects <- c("01", "02", "03", "04", "05", "06", "07", "08", "09", "10", "11", "12", "13", "14",
-              "16", "17", "18", "20")
+subjects <- list.files('data/raw/beh/', pattern="json") %>% 
+  str_extract("[0-9]*.json") %>%
+  str_remove(".json")
 
 for(subject in subjects){
   

### 2024-02-22 manuscript.qmd
working on regression-based artifact correction

@@
 ```{r}
-#| Libraries
+#| label: Load libraries
 #| include: false
@@
 library(ggplot2)
+library(osfr)
 ```
@@
 ```{r}
-#| Download the data from the OSF
-
+#| label: Download the data from the OSF
+osf_retrieve_node("ngtha") %>%
+  osf_ls_files() %>%
+  osf_download(path="data/final", conflicts="skip")
 ```
@@
 ```{r}
-#| Check accuracy
+#| label: Check accuracy
 #| include: false
@@
 ```{r}
-#| label: Behavioral pop-out effect
+#| label: fig-beh-pop-out
 
@@
 #| label: model the GEE
+#| include: false
 
@@
 ```{r}
-#| Load eeg data
+#| label: Load eeg data
 #| include: false
 
-eeg_data <- read_csv("data/final/eeg.csv") %>%
+eeg_data <- read_csv("data/final/eeg.csv", col_types = "cdcllcdlc") %>%
   filter(!subject %in% excluded_subjects)
@@
 ```{r}
+#| label: fig-grand-averages
+#| fig-width: 10
+#| fig-height: 8
 ggplot(grand_average, aes(x=t, y=M, color=is_word, linetype=word_category)) +

### 2024-02-22 preprocessing/extract-events.R

@@ -60,8 +60,8 @@ extract_events <- function(eeg.file, beh.file){
   # indicating that the experimenter dragged the window 
   # under the sensor after starting recording
   
-  while(filtered.events$time[2] - filtered.events$time[1] > 10){
-    # remove the first row
+  while(filtered.events$time[5] - filtered.events$time[1] > 25){
+    # remove the first ro
     filtered.events <- filtered.events %>%
       slice(-1) %>%
       mutate(row_id = 1:n())

### 2024-02-22 preprocessing/mege-local.R

@@ -5,9 +5,10 @@ library(dplyr)
 
 files <- list.files("data/preprocessed", pattern = "*.csv", full.names = TRUE)
 data <- lapply(files, function(x){
-  read_csv(x, col_types = "cdcllcddddllc")
+  read_csv(x, col_types = "cdcllcdddllc") %>% 
+    dplyr::filter(electrode %in% c("Cz", "Pz")) %>%
+    select(-v_range, -eye_range, -eyeblink)
 }) %>% 
-  bind_rows() %>% 
-  dplyr::filter(electrode %in% c("Cz", "Pz"))
+  bind_rows()
 
 write_csv(data, "data/final/eeg.csv")

### 2024-02-22 preprocessing/preprocessing-eeg-functions.R

@@ -5,13 +5,13 @@ library(ravetools)
 library(eegkit)
 source('preprocessing/extract-events.R')
 
-preprocess_eeg <- function(file, beh.file, subject_id, sampling_rate=500, filter_low=0.1, filter_high=70, notch_filter_low=59, notch_filter_high=61, segment_begin=-100, segment_end=1000, segment_offset=0, bad_segment_range=200, which_electrodes=c('Cz', 'Fz', 'Fp1', 'Fp2')){
+preprocess_eeg <- function(file, beh.file, subject_id, sampling_rate=500, filter_low=0.1, filter_high=70, notch_filter_low=59, notch_filter_high=61, segment_begin=-100, segment_end=1000, segment_offset=0, bad_segment_range=200, eye_threshold=70, which_electrodes=c('Cz', 'Fz', 'Fp1', 'Fp2')){
   data <- read_eeg_tidy(eeg.file, beh.file, which_electrodes) %>%
     #linked_ears_rereference() %>%
     bandpass(low=filter_low, high=filter_high, sampling_rate=sampling_rate) %>%
-    notch(low=notch_filter_low, high=notch_filter_high, sampling_rate=sampling_rate) %>%
+    #notch(low=notch_filter_low, high=notch_filter_high, sampling_rate=sampling_rate) %>%
     segment(start = segment_begin, end = segment_end, offset=segment_offset, sampling_rate=sampling_rate) %>%
-    artifact_rejection(max_range=bad_segment_range) %>%
+    artifact_rejection(max_range=bad_segment_range, eye_threshold = eye_threshold) %>%
     baseline_correct() %>%
     mutate(subject = subject_id)
   
@@ -33,7 +33,8 @@ read_eeg_tidy <- function(eeg.file, beh.file, which_electrodes=NA) {
   data$TRIGGER <- NULL
   
   tidy_data <- pivot_longer(data, 1:19, names_to = "electrode", values_to = "v") %>% 
-    select(sample_id, electrode, v, A2) 
+    select(sample_id, electrode, v, A2) %>%
+    select(-A2) #because we are not doing linked ear re-referencing
   
   if(!any(is.na(which_electrodes))){
     tidy_data <- tidy_data %>% dplyr::filter(electrode %in% which_electrodes)
@@ -57,7 +58,7 @@ bandpass <- function(data, low, high, sampling_rate){
   df <- data$signals
   df <- df %>% 
     group_by(electrode) %>% 
-    mutate(v = eegfilter(v, sampling_rate, low, high)) %>%
[…]

### 2024-02-22 preprocessing/run_preprocessing_local_machine.R

@@ -24,13 +24,14 @@ for(subject in subjects){
       subject_id = subject,
       sampling_rate = 500,
       filter_low = 0.1,
-      filter_high = 70,
+      filter_high = 30,
       notch_filter_low = 59,
       notch_filter_high = 61,
       segment_begin = -200,
       segment_end = 1000,
       segment_offset = 0,
-      bad_segment_range = 200,
+      bad_segment_range = 500,
+      eye_threshold = 70,
       which_electrodes = c("Fp1", "Fp2", "Cz", "Pz"))
     
     write_csv(preprocessed.data, file=paste0("data/preprocessed/subject-", subject,"-epochs.csv"))

### 2024-02-22 tmp for testing.R

@@ -1,0 +1,26 @@
+source("preprocessing/preprocessing-eeg-functions.R")
+
+subject <- "01"
+
+eeg.file <- list.files('data/raw/eeg', pattern=paste0("subject-", subject), full.names = T)
+beh.file <- paste0('data/raw/beh/219_2024_behavioral_', subject,'.json')
+
+sampling_rate = 500
+filter_low = 0.1
+filter_high = 30
+segment_begin = -200
+segment_end = 1000
+segment_offset = 0
+bad_segment_range = 500
+eye_threshold = 70
+which_electrodes = c("Fp1", "Fp2", "Cz", "Pz")
+eye_channels=c("Fp1", "Fp2")
+target_channels=c("Cz", "Pz")
+
+epochs <- read_eeg_tidy(eeg.file, beh.file, which_electrodes) %>%
+  #linked_ears_rereference() %>%
+  bandpass(low=filter_low, high=filter_high, sampling_rate=sampling_rate) %>%
+  #notch(low=notch_filter_low, high=notch_filter_high, sampling_rate=sampling_rate) %>%
+  segment(start = segment_begin, end = segment_end, offset=segment_offset, sampling_rate=sampling_rate)
+
+

### 2024-02-23 manuscript.qmd
rt analysis

@@
 ```{r}
+#| label: Compute response time differences for words
+#| include: false
+
+subject_level_rt <- behavioral_data_test_set %>%
+  filter(correct == TRUE) %>%
+  group_by(subject_id, word_category, category, is_word) %>%
+  summarize(rt = mean(rt, na.rm = TRUE))
+```
+
+```{r}
+behavioral_pop_out_data <- subject_level_rt %>%
+  filter(is_word == TRUE)
+
+ggplot(behavioral_pop_out_data, aes(x=word_category, y=rt, group=subject_id))+
+  geom_point()+
+  geom_line()+
+  #labs(x="Word Type", y="Accuracy")+
+  facet_grid(.~category)+
+  theme_bw()
+```
+
+```{r}
+m <- gee(rt ~ word_category,
+    id = subject_id,
+    subset = is_word == TRUE & correct == TRUE & category == "moral",
+    data = behavioral_data_test_set,
+    family = gaussian,
+    corstr = "exchangeable")
+
+summary(m)
+```
+
+```{r}
 #| label: Load eeg data

### 2024-03-12 preprocessing/preprocessing-eeg-functions.R
using a triangle filter for eye blink points

@@ -111,21 +111,27 @@ eyeblink_detector_step <- function(v, window_size=200, sampling_rate=500){
   return(max.diff)
 }
 
-eyeblink_points <- function(v, blink_criteria=15, sampling_rate=500, window_ms=200){
+#v <- eyes %>% dplyr::filter(event_id == 409) %>% pull(v)
+
+eyeblink_points <- function(v, blink_criteria=10, sampling_rate=500, window_ms=200){
   window_length <- window_ms * (sampling_rate/1000)
   half_window <- window_length / 2
-  blink_cov <- c(rep(+1, half_window), rep(-1, half_window))
+  blink_cov <- c(seq(-1, 1, length.out=half_window), seq(1, -1, length.out=half_window))
+  # look for rise and then fall
   cv <- stats::filter(v, blink_cov, method="convolution", sides=2) / length(blink_cov)
-  blink_pts <- abs(cv) >= blink_criteria
-  blink_group <- cumsum(c(0, abs(diff(as.integer(blink_pts)))))
-  blink_mean <- mean(v[blink_pts])
+  blink_idx <- which(cv > blink_criteria)
   
-  blink.df <- data.frame(v=v, is_blinking=blink_pts, blink_group=blink_group)
+  margin <- round(half_window / 2)
+  blink_idx <- sapply(blink_idx, function(x){
+    return(seq(x-margin, x+margin))
+  }) %>% as.numeric() %>% unique()
+  
+  blink.df <- data.frame(x=1:length(v), v=v)
   blink.df <- blink.df %>% 
-    group_by(blink_group) %>%
-    mutate(blink_group_avg=mean(v)) %>%
-    ungroup() %>%
-    mutate(is_blinking = is_blinking | blink_group_avg > blink_mean)
+    mutate(is_blinking = x %in% blink_idx)
+  
+  ggplot(blink.df, aes(x=x, y=v, color=is_blinking)) +
+    geom_point()
   
   return(blink.df %>% pull(is_blinking))
 }
@@ -143,14 +149,14 @@ eyeblink_removal_with_regression <- function(epochs, eye_channels=c("Fp1", "Fp2"
   
   eyeblinks <- eyes %>%
     group_by(event_id) %>%
-    mutate(is_blinking = eyeblink_points(v, blink_criteria=15, sampling_rate=500, window_ms=200)) %>%
[…]

### 2024-03-13 preprocessing/preprocessing-eeg-functions.R
work on blink detection and regression

@@ -138,22 +138,23 @@ eyeblink_points <- function(v, blink_criteria=10, sampling_rate=500, window_ms=2
 
 eyeblink_removal_with_regression <- function(epochs, eye_channels=c("Fp1", "Fp2"), target_channels=c("Cz", "Pz")){
   
-  # compute a single average for the eye channels for each condition
-  eyes <- epochs %>% 
-    dplyr::filter(electrode %in% eye_channels) %>%
-    group_by(event_id, word_type, is_word, t) %>%
-    summarize(v = mean(v))
+
   
   # identify all time points that include an eyeblink
   # we will use this to remove the eyeblink from the target channels
-  
-  eyeblinks <- eyes %>%
+  single_eye_channel_with_blinks <- epochs %>% 
+    dplyr::filter(electrode %in% eye_channels) %>%
+    group_by(event_id, t) %>%
+    summarize(v = mean(v)) %>%
     group_by(event_id) %>%
-    mutate(is_blinking = eyeblink_points(v, blink_criteria=15, sampling_rate=500, window_ms=200))
+    mutate(is_blinking = eyeblink_points(v, blink_criteria=15, sampling_rate=500, window_ms=200)) %>%
+    ungroup()
   
-  eyeblink_binary <- eyeblinks %>% 
-    group_by(event_id) %>%
-    summarize(eyeblink = any(is_blinking))
+  # compute a single average for the eye channels for each condition
+  eyes_average <- single %>% 
+    dplyr::filter(electrode %in% eye_channels) %>%
+    group_by(event_id, word_type, is_word, t) %>%
+    summarize(v = mean(v))
   
   # eyes <- eyes %>%
   #   left_join(eyeblinks, by="event_id")

### 2024-03-14 manuscript.qmd
Update preprocessing to remove edge effects and filter segments with a bad channel.
Update manuscript.

@@
 library(osfr)
+library(gee)
+library(tidyr)
 ```
+
+# Introduction
+
+This is a replication of the study by Gantman et al. (2014). Replications are important for *reasons*.
+
+# Methods
 
@@
 #| label: Download the data from the OSF
+#| include: false
 osf_retrieve_node("ngtha") %>%
@@
 ```
+
+## Participants
 
@@
 ```{r}
-#| label: Flip responses for subject 01
+#| label: Flip responses for subject 01, 36 moral words
 #| include: false
@@
 behavioral_data <- behavioral_data %>%
-  mutate(correct = ifelse(subject_id == "01", !correct, correct))
+  mutate(correct = ifelse(subject_id == "01", !correct, correct)) %>%
+  mutate(correct = ifelse(subject_id == "36" & phase == "moral", !correct, correct))
 ```
@@
 ```{r}
+#| label: Count the number of subjects and subjects remaining
+#| include: false
+
+n_subjects <- behavioral_data %>% pull(subject_id) %>% unique() %>% length()
+
+n_subjects_remaining <- behavioral_data_filtered %>% pull(subject_id) %>% unique() %>% length()
+```
+
+`r n_subjects` subjects were recruited for the study.
+After applying the exclusion criteria, `r n_subjects_remaining` subjects remain.
+`r length(exclude_for_fashion_twice_subjects)` subjects were excluded for receiving fashion words twice due to a technical error, `r length(exclude_for_non_response_subjects)` subjects were excluded for having a non-response rate greater than 50%, and `r length(exclude_for_non_word_response_subjects)` subjects were excluded for having a non-word response rate greater than 90%.
+
+# Results
+
+## Behavioral
+
+```{r}
 #| label: Select relevant test data
@@
   group_by(subject_id, word_category, category, is_word) %>%
-  summarise(accuracy = mean(correct))
+  summarise(accuracy = mean(correct), se=sd(correct)/sqrt(n()))
 ```
@@
 #| label: fig-beh-pop-out
+#| fig-cap: Accuracy for word trials in the fashion and moral conditions showed that performance was much higher than expected.
+We later discovered this was due to a difference in procedure between our study and the original study.
 
 behavioral_pop_out_data <- subject_level_accuracy %>%
-  filter(is_word == TRUE)
+  filter(is_word == TRUE) %>%
+  pivot_wider(names_from = word_category, values_from = c(accuracy, se))
 
-ggplot(behavioral_pop_out_data, aes(x=word_category, y=accuracy, group=subject_id))+
+ggplot(behavioral_pop_out_data, aes(x=`accuracy_non-category`, y=`accuracy_category`))+
   geom_point()+
-  geom_line()+
-  #labs(x="Word Type", y="Accuracy")+
-  facet_grid(.~category)+
-  theme_bw()
+  geom_linerange(aes(ymin=`accuracy_category`-`se_category`, ymax=`accuracy_category`+`se_category`), size=0.25)+
+  geom_linerange(aes(xmin=`accuracy_non-category`-`se_non-category`, xmax=`accuracy_non-category`+`se_non-category`), size=0.25, alpha=0.3)+
+  labs(x="Accuracy for non-category words", y="Accuracy for category words")+
+  facet_grid(.~category, labeller = as_labeller(c("fashion"="Fashion Words", "moral"="Moral Words")))+ 
+  geom_abline(intercept = 0, slope = 1, linetype="dashed")+
+  coord_cartesian(xlim=c(0.5,1), ylim=c(0.5,1))+
+  theme_bw(base_size=12)+
+  theme(aspect.ratio=1, panel.grid=element_blank())
 ```
@@
 ```{r}
-#| label: model the GEE
+#| label: Models for pop out effects
 #| include: false
 
-library(gee)
-
-m <- gee(correct ~ word_category,
+behavioral_model_moral_pop_out <- gee(correct ~ word_category,
     id = subject_id,
@@
     family = binomial,
-    corstr = "exchangeable")
+    corstr = "exchangeable") %>% summary()
 
-summary(m)
+coefficient_moral_pop_out <- behavioral_model_moral_pop_out$coefficients[2, 'Estimate']
+coefficient_moral_pop_out_se <- behavioral_model_moral_pop_out$coefficients[2, 'Robust S.E.']
+z_moral_pop_out <- behavioral_model_moral_pop_out$coefficients[2, 'Robust z']
+p_moral_pop_out <- z_moral_pop_out %>% pnorm(lower.tail = FALSE)
+
+fashion_model_moral_pop_out <- gee(correct ~ word_category,
+    id = subject_id,
+    subset = is_word == TRUE & category == "fashion",
+    data = behavioral_data_test_set,
+    family = binomial,
+    corstr = "exchangeable") %>% summary()
+
+coefficient_fashion_pop_out <- fashion_model_moral_pop_out$coefficients[2, 'Estimate']
+coefficient_fashion_pop_out_se <- fashion_model_moral_pop_out$coefficients[2, 'Robust S.E.']
+z_fashion_pop_out <- fashion_model_moral_pop_out$coefficients[2, 'Robust z']
+p_fashion_pop_out <- z_fashion_pop_out %>% pnorm(lower.tail = FALSE)
 ```
+
+Accuracy for moral words was not significantly different between category and non-category words, $b = `r coefficient_moral_pop_out`$, $SE = `r coefficient_moral_pop_out_se`$, $z = `r z_moral_pop_out`$, $p = `r p_moral_pop_out`$.
+Accuracy for fashion words was significantly different between category and non-category words, $b = `r coefficient_fashion_pop_out`$, $SE = `r coefficient_fashion_pop_out_se`$, $z = `r z_fashion_pop_out`$, $p = `r p_fashion_pop_out`$.
 
@@
 ```{r}
+#| include: false
+
 behavioral_pop_out_data <- subject_level_rt %>%
@@
 ```{r}
+#| include: false
+
 m <- gee(rt ~ word_category,
@@
 
+## EEG
+
 ```{r}
@@
 
-eeg_data <- read_csv("data/final/eeg.csv", col_types = "cdcllcdlc") %>%
-  filter(!subject %in% excluded_subjects)
+eeg_data <- read_csv("data/final/eeg.csv", col_types = "cdcllcdc") %>%
+  filter(!subject %in% excluded_subjects) %>%
+  filter(subject != "34") # really few usable segments
 ```
@@
 eeg_data <- eeg_data %>%
-  mutate(correct = ifelse(subject == "01", !correct, correct))
+  mutate(correct = ifelse(subject == "01", !correct, correct)) %>%
+  mutate(correct = ifelse(subject == "36" & word_type == "moral", !correct, correct))
 ```
@@
 subject_eeg <- eeg_data %>%
-  filter(good_segment == TRUE) %>%
   filter(electrode %in% c("Cz", "Pz")) %>%
@@
   group_by(t, electrode, word_category, category, is_word) %>%
-  summarize(M = weighted.mean(v, n), SE = sd(v)/sqrt(n()))
+  summarize(M = mean(v), SE = sd(v)/sqrt(n()))
 ```
@@
 ```{r}
+#| label: Count the number of good segments per subject
+#| include: false
 count_good_trials <- eeg_data %>%
-  dplyr::filter(good_segment == TRUE) %>%
-  dplyr::filter(electrode %in% c("Cz", "Pz")) %>%
-  group_by(subject, electrode, word_type, is_word, event_id) %>%
-  slice(1) %>%
-  group_by(subject, electrode, word_type, is_word) %>%
-  summarize(n = n())
+  filter(t==0, electrode=="Cz") %>%
+  group_by(subject) %>%
+  summarize(n=n()) %>%
+  mutate(percent = (n/600)*100)
 
-count_good_trials
+mean_good_trials <- mean(count_good_trials$n)
+sd_good_trials <- sd(count_good_trials$n)
+
 ```
+
+```{r}
+#| label: Define time windows
+#| include: false
+p2.window.start <- 200
+p2.window.end <- 250
+n2.window.start <- 250
+n2.window.end <- 350
+p3.window.start <- 350
+p3.window.end <- 600
+lpp.window.start <- 600
+lpp.window.end <- 800
+
+# vectorized function for indicating time window
+get_time_window <- function(t){
+  ifelse(t >= p2.window.start & t < p2.window.end, "p2",
+  ifelse(t >= n2.window.start & t < n2.window.end, "n2",
+  ifelse(t >= p3.window.start & t < p3.window.end, "p3",
+  ifelse(t >= lpp.window.start & t < lpp.window.end, "lpp",
+  "other"))))
+}
+```
+
+```{r}
+```
+
+```{r}
+#| label: Calculate mean voltage in all time windows for each trial
+#| include: false
+
+time_window_data <- eeg_data %>%
+  filter(electrode %in% c("Cz", "Pz")) %>%
+  mutate(erp_component = get_time_window(t)) %>%
+  filter(erp_component != "other") %>%
+  group_by(subject, electrode, word_type, is_word, erp_component) %>%
+  summarize(v = mean(v)) %>%
+  mutate(word_category = ifelse(word_type %in% c("fashion", "moral"), "category", "non-category"),
+         category = ifelse(word_type %in% c("fashion", "non-fashion"), "fashion", "moral"))
+```
+
+```{r}
+#| label: Run GEE models for all time windows, fashion data pop-out
+#| include: false
+
+p2_model <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "p2" & category == "fashion" & is_word == TRUE & electrode == "Cz",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p2_model$coefficients
+
+n2_model <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "n2" & category == "fashion"& is_word == TRUE & electrode == "Cz",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+n2_model$coefficients
+
+p3_model <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "p3" & category == "fashion"& is_word == TRUE & electrode == "Cz",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p3_model$coefficients
+
+lpp_model <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "lpp" & category == "fashion"& is_word == TRUE & electrode == "Cz",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+lpp_model$coefficients
+```
+```{r}
+#| label: Run GEE models for all time windows, moral data pop-out
+#| include: false
+
+p2_model <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "p2" & category == "moral" & is_word == TRUE & electrode == "Cz",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p2_model$coefficients
+
+n2_model <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "n2" & category == "moral" & is_word == TRUE & electrode == "Cz",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+n2_model$coefficients
+
+p3_model <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "p3" & category == "moral"& is_word == TRUE & electrode == "Cz",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p3_model$coefficients
+
+lpp_model <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "lpp" & category == "moral"& is_word == TRUE & electrode == "Cz",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+lpp_model$coefficients
+```
+
+```{r}
+#| label: Run GEE models for all time windows, moral data word non-word
+#| include: false
+
+p2_model <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "p2" & category == "moral",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p2_model$coefficients
+
+n2_model <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "n2" & category == "moral",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+n2_model$coefficients
+
+p3_model <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "p3" & category == "moral",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p3_model$coefficients
+
+lpp_model <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "lpp" & category == "moral",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+lpp_model$coefficients
+
+```
+
+```{r}
+#| label: Run GEE models for all time windows, fashion data word non-word
+#| include: false
+
+p2_model <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "p2" & category == "fashion",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p2_model$coefficients
+
+n2_model <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "n2" & category == "fashion",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+n2_model$coefficients
+
+p3_model <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "p3" & category == "fashion",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p3_model$coefficients
+
+lpp_model <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "lpp" & category == "fashion",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+lpp_model$coefficients
+
+```

### 2024-03-14 preprocessing/mege-local.R

@@ -5,9 +5,9 @@ library(dplyr)
 
 files <- list.files("data/preprocessed", pattern = "*.csv", full.names = TRUE)
 data <- lapply(files, function(x){
-  read_csv(x, col_types = "cdcllcdddllc") %>% 
+  read_csv(x, col_types = "cdcllcddlc") %>% 
     dplyr::filter(electrode %in% c("Cz", "Pz")) %>%
-    select(-v_range, -eye_range, -eyeblink)
+    select(-v_range, -good_segment)
 }) %>% 
   bind_rows()
 

### 2024-03-14 preprocessing/preprocessing-eeg-functions.R

@@ -11,8 +11,16 @@ preprocess_eeg <- function(file, beh.file, subject_id, sampling_rate=500, filter
     bandpass(low=filter_low, high=filter_high, sampling_rate=sampling_rate) %>%
     #notch(low=notch_filter_low, high=notch_filter_high, sampling_rate=sampling_rate) %>%
     segment(start = segment_begin, end = segment_end, offset=segment_offset, sampling_rate=sampling_rate) %>%
-    artifact_rejection(max_range=bad_segment_range, eye_threshold = eye_threshold) %>%
+    large_anomaly_removal(max_range=1000) %>%
+    filter_epochs_with_bad_channels(expected_channels = 4) %>%
+    baseline_correct(start_baseline=-200) %>%
+    eyeblink_removal_with_regression(eye_channels=c("Fp1", "Fp2"), target_channels=c("Cz", "Pz"), blink_criteria=10, sampling_rate=sampling_rate, windows_ms=200) %>%
+    change_segment_range(start_time=-200, end_time=1000) %>%
+    large_anomaly_removal(max_range=500) %>%
+    filter_epochs_with_bad_channels(expected_channels = 2) %>%
     baseline_correct() %>%
+    #artifact_rejection(max_range=bad_segment_range, eye_threshold = eye_threshold) %>%
+    
     mutate(subject = subject_id)
   
   return(data)
@@ -130,43 +138,44 @@ eyeblink_points <- function(v, blink_criteria=10, sampling_rate=500, window_ms=2
   blink.df <- blink.df %>% 
     mutate(is_blinking = x %in% blink_idx)
   
-  ggplot(blink.df, aes(x=x, y=v, color=is_blinking)) +
-    geom_point()
+  # ggplot(blink.df, aes(x=x, y=v, color=is_blinking)) +
+  #   geom_point()
   
   return(blink.df %>% pull(is_blinking))
 }
 
-eyeblink_removal_with_regression <- function(epochs, eye_channels=c("Fp1", "Fp2"), target_channels=c("Cz", "Pz")){
+large_anomaly_removal <- function(epochs, max_range=1000){
+  d <- epochs %>% 
+    group_by(event_id, electrode) %>%
+    summarize(v_range = max(v) - min(v))
   
+  good.segments <- d %>% 
+    group_by(event_id) %>%
+    mutate(good_segment = v_range <= max_range) %>%
+    ungroup()
+  
+  epochs.ar <- epochs %>%
[…]

### 2024-03-14 preprocessing/run_preprocessing_local_machine.R

@@ -27,8 +27,8 @@ for(subject in subjects){
       filter_high = 30,
       notch_filter_low = 59,
       notch_filter_high = 61,
-      segment_begin = -200,
-      segment_end = 1000,
+      segment_begin = -400,
+      segment_end = 1200,
       segment_offset = 0,
       bad_segment_range = 500,
       eye_threshold = 70,

### 2024-03-15 manuscript.qmd
first draft of a complete analysis

@@
 
-This is a replication of the study by Gantman et al. (2014). Replications are important for *reasons*.
+This is a replication of the study by Gantman et al. (2020). Replications are important for *reasons*.
 
@@
 
-`r n_subjects` subjects were recruited for the study.
+`r n_subjects` subjects participated in the study.
 After applying the exclusion criteria, `r n_subjects_remaining` subjects remain.
@@
 #| label: fig-beh-pop-out
-#| fig-cap: Accuracy for word trials in the fashion and moral conditions showed that performance was much higher than expected.
+#| fig-cap: Performance for in-category words and out-of-category words for each participant.
+Points above the diagonal represent higher accuracy for in-category words.
+Overall accuracy was much higher than expected.
 We later discovered this was due to a difference in procedure between our study and the original study.
+Lines represent +/- 1 SE.
+#| echo: false
 
@@
   geom_point()+
-  geom_linerange(aes(ymin=`accuracy_category`-`se_category`, ymax=`accuracy_category`+`se_category`), size=0.25)+
-  geom_linerange(aes(xmin=`accuracy_non-category`-`se_non-category`, xmax=`accuracy_non-category`+`se_non-category`), size=0.25, alpha=0.3)+
+  geom_linerange(aes(ymin=`accuracy_category`-`se_category`, ymax=`accuracy_category`+`se_category`), linewidth=0.25)+
+  geom_linerange(aes(xmin=`accuracy_non-category`-`se_non-category`, xmax=`accuracy_non-category`+`se_non-category`), linewidth=0.25, alpha=0.3)+
   labs(x="Accuracy for non-category words", y="Accuracy for category words")+
@@
 z_moral_pop_out <- behavioral_model_moral_pop_out$coefficients[2, 'Robust z']
-p_moral_pop_out <- z_moral_pop_out %>% pnorm(lower.tail = FALSE)
+p_moral_pop_out <- (1 - pnorm(abs(z_moral_pop_out))) * 2
 
@@
 z_fashion_pop_out <- fashion_model_moral_pop_out$coefficients[2, 'Robust z']
-p_fashion_pop_out <- z_fashion_pop_out %>% pnorm(lower.tail = FALSE)
+p_fashion_pop_out <- (1 - pnorm(abs(z_fashion_pop_out))) * 2
+
+mean_moral_in_category <- subject_level_accuracy %>%
+  filter(is_word == TRUE & category == "moral" & word_category == "category") %>%
+  pull(accuracy) %>%
+  mean() %>% 
+  round(4)* 100
+
+mean_moral_out_category <- subject_level_accuracy %>%
+  filter(is_word == TRUE & category == "moral" & word_category == "non-category") %>%
+  pull(accuracy) %>%
+  mean() %>% 
+  round(4)* 100
+
+mean_fashion_in_category <- subject_level_accuracy %>%
+  filter(is_word == TRUE & category == "fashion" & word_category == "category") %>%
+  pull(accuracy) %>%
+  mean() %>% 
+  round(4)* 100
+
+mean_fashion_out_category <- subject_level_accuracy %>%
+  filter(is_word == TRUE & category == "fashion" & word_category == "non-category") %>%
+  pull(accuracy) %>%
+  mean() %>% 
+  round(4)* 100
 ```
 
-Accuracy for moral words was not significantly different between category and non-category words, $b = `r coefficient_moral_pop_out`$, $SE = `r coefficient_moral_pop_out_se`$, $z = `r z_moral_pop_out`$, $p = `r p_moral_pop_out`$.
-Accuracy for fashion words was significantly different between category and non-category words, $b = `r coefficient_fashion_pop_out`$, $SE = `r coefficient_fashion_pop_out_se`$, $z = `r z_fashion_pop_out`$, $p = `r p_fashion_pop_out`$.
+We found a pop-out effect for both moral and fashion words.
+In the moral condition, participants were `r mean_moral_in_category`% accurate for moral words and `r mean_moral_out_category`% accurate for non-moral words.
+This difference was statistically significant in the GEE model, $\beta$ = `r coefficient_moral_pop_out %>% round(3)`, *SE* = `r coefficient_moral_pop_out_se %>% round(3)`, *z* = `r z_moral_pop_out %>% round(3)`, *p* = `r p_moral_pop_out %>% format(scientific=FALSE)`.
 
-```{r}
-#| label: Compute response time differences for words
-#| include: false
-
-subject_level_rt <- behavioral_data_test_set %>%
-  filter(correct == TRUE) %>%
-  group_by(subject_id, word_category, category, is_word) %>%
-  summarize(rt = mean(rt, na.rm = TRUE))
-```
-
-```{r}
-#| include: false
-
-behavioral_pop_out_data <- subject_level_rt %>%
-  filter(is_word == TRUE)
-
-ggplot(behavioral_pop_out_data, aes(x=word_category, y=rt, group=subject_id))+
-  geom_point()+
-  geom_line()+
-  #labs(x="Word Type", y="Accuracy")+
-  facet_grid(.~category)+
-  theme_bw()
-```
-
-```{r}
-#| include: false
-
-m <- gee(rt ~ word_category,
-    id = subject_id,
-    subset = is_word == TRUE & correct == TRUE & category == "moral",
-    data = behavioral_data_test_set,
-    family = gaussian,
-    corstr = "exchangeable")
-
-summary(m)
-```
+In the fashion condition, participants were `r mean_fashion_in_category`% accurate for fashion words and `r mean_fashion_out_category`% accurate for non-fashion words.
+This difference was statistically significant in the GEE model, $\beta$ = `r coefficient_fashion_pop_out`, *SE* = `r coefficient_fashion_pop_out_se %>% round(3)`, *z* = `r z_fashion_pop_out %>% round(3)`, *p* = `r p_fashion_pop_out %>% format(scientific=FALSE)`.
 
@@
 ```{r}
+#| label: Grand average computation
+#| include: false
+
 grand_average <- subject_eeg %>%
@@
 #| fig-height: 8
+#| fig-cap: Grand average waveforms. Shaded areas represent +/- 1 SE.
+#| echo: false
+
 ggplot(grand_average, aes(x=t, y=M, color=is_word, linetype=word_category)) +
@@
   scale_x_continuous(breaks=c(0,500, 1000))+
-  facet_grid(electrode~category)+
+  scale_color_brewer(palette="Set1", name="Is word?", labels=c("Non-word", "Word"))+
+  scale_fill_brewer(palette="Set1", name="Is word?", labels=c("Non-word", "Word"))+
+  scale_linetype_manual(name="Word Category", labels=c("Moral/Fashion", "Non-Moral/Non-Fashion"), values=c("solid", "dashed"))+
+  facet_grid(electrode~category, labeller=as_labeller(c("fashion"="Fashion Words", "moral"="Moral Words", "Cz"="Cz", "Pz"="Pz" )))+
   labs(x="Time since word onset (ms)", y="Voltage (uV)", color="Is word?", fill="Is word?", linetype="Word Category")+
-  theme_minimal()+
+  theme_minimal(base_size=12)+
   theme(panel.grid = element_blank())
@@
 #| include: false
+
 count_good_trials <- eeg_data %>%
@@
 ```{r}
-```
-
-```{r}
 #| label: Calculate mean voltage in all time windows for each trial
@@
 
+### Words vs. Non-Words
+
+Following Gantman and Van Bavel, we looked for word vs. non-word ERP effects at each time window at electrode Pz.
+
+```{r}
+#| label: Run GEE models for all time windows, moral data word non-word
+#| include: false
+
+p2_model_moral_word_nonword <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "p2" & category == "moral" & electrode == "Pz",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p2_model_moral_word_nonword_beta <- p2_model_moral_word_nonword$coefficients[2, 'Estimate']
+p2_model_moral_word_nonword_se <- p2_model_moral_word_nonword$coefficients[2, 'Robust S.E.']
+p2_model_moral_word_nonword_z <- p2_model_moral_word_nonword$coefficients[2, 'Robust z']
+p2_model_moral_word_nonword_p <- (1 - pnorm(abs(p2_model_moral_word_nonword_z))) * 2
+
+n2_model_moral_word_nonword <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "n2" & category == "moral" & electrode == "Pz",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+n2_model_moral_word_nonword_beta <- n2_model_moral_word_nonword$coefficients[2, 'Estimate']
+n2_model_moral_word_nonword_se <- n2_model_moral_word_nonword$coefficients[2, 'Robust S.E.']
+n2_model_moral_word_nonword_z <- n2_model_moral_word_nonword$coefficients[2, 'Robust z']
+n2_model_moral_word_nonword_p <- (1 - pnorm(abs(n2_model_moral_word_nonword_z))) * 2
+
+p3_model_moral_word_nonword <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "p3" & category == "moral" & electrode == "Pz",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p3_model_moral_word_nonword_beta <- p3_model_moral_word_nonword$coefficients[2, 'Estimate']
+p3_model_moral_word_nonword_se <- p3_model_moral_word_nonword$coefficients[2, 'Robust S.E.']
+p3_model_moral_word_nonword_z <- p3_model_moral_word_nonword$coefficients[2, 'Robust z']
+p3_model_moral_word_nonword_p <- (1 - pnorm(abs(p3_model_moral_word_nonword_z))) * 2
+
+lpp_model_moral_word_nonword <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "lpp" & category == "moral" & electrode == "Pz",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+lpp_model_moral_word_nonword_beta <- lpp_model_moral_word_nonword$coefficients[2, 'Estimate']
+lpp_model_moral_word_nonword_se <- lpp_model_moral_word_nonword$coefficients[2, 'Robust S.E.']
+lpp_model_moral_word_nonword_z <- lpp_model_moral_word_nonword$coefficients[2, 'Robust z']
+lpp_model_moral_word_nonword_p <- (1 - pnorm(abs(lpp_model_moral_word_nonword_z))) * 2
+```
+
+In the moral condition, words elicited a more positive ERP in the P2 window ($\beta$ = `r p2_model_moral_word_nonword_beta %>% round(3)`, *SE* = `r p2_model_moral_word_nonword_se %>% round(3)`, *z* = `r p2_model_moral_word_nonword_z %>% round(3)`, *p* = `r p2_model_moral_word_nonword_p %>% format(scientific=FALSE)`), N2 window ($\beta$ = `r n2_model_moral_word_nonword_beta %>% round(3)`, *SE* = `r n2_model_moral_word_nonword_se %>% round(3)`, *z* = `r n2_model_moral_word_nonword_z %>% round(3)`, *p* = `r n2_model_moral_word_nonword_p %>% format(scientific=FALSE)`), and P3 window ($\beta$ = `r p3_model_moral_word_nonword_beta %>% round(3)`, *SE* = `r p3_model_moral_word_nonword_se %>% round(3)`, *z* = `r p3_model_moral_word_nonword_z %>% round(3)`, *p* = `r p3_model_moral_word_nonword_p %>% format(scientific=FALSE)`).
+There was no significant effect in the LPP window ($\beta$ = `r lpp_model_moral_word_nonword_beta %>% round(3)`, *SE* = `r lpp_model_moral_word_nonword_se %>% round(3)`, *z* = `r lpp_model_moral_word_nonword_z %>% round(3)`, *p* = `r lpp_model_moral_word_nonword_p %>% format(scientific=FALSE)`).
+
+```{r}
+#| label: Run GEE models for all time windows, fashion data word non-word
+#| include: false
+
+p2_model_fashion_word_nonword <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "p2" & category == "fashion" & electrode == "Pz",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p2_model_fashion_word_nonword_beta <- p2_model_fashion_word_nonword$coefficients[2, 'Estimate']
+p2_model_fashion_word_nonword_se <- p2_model_fashion_word_nonword$coefficients[2, 'Robust S.E.']
+p2_model_fashion_word_nonword_z <- p2_model_fashion_word_nonword$coefficients[2, 'Robust z']
+p2_model_fashion_word_nonword_p <- (1 - pnorm(abs(p2_model_fashion_word_nonword_z))) * 2
+
+n2_model_fashion_word_nonword <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "n2" & category == "fashion" & electrode == "Pz",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+n2_model_fashion_word_nonword_beta <- n2_model_fashion_word_nonword$coefficients[2, 'Estimate']
+n2_model_fashion_word_nonword_se <- n2_model_fashion_word_nonword$coefficients[2, 'Robust S.E.']
+n2_model_fashion_word_nonword_z <- n2_model_fashion_word_nonword$coefficients[2, 'Robust z']
+n2_model_fashion_word_nonword_p <- (1 - pnorm(abs(n2_model_fashion_word_nonword_z))) * 2
+
+p3_model_fashion_word_nonword <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "p3" & category == "fashion" & electrode == "Pz",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p3_model_fashion_word_nonword_beta <- p3_model_fashion_word_nonword$coefficients[2, 'Estimate']
+p3_model_fashion_word_nonword_se <- p3_model_fashion_word_nonword$coefficients[2, 'Robust S.E.']
+p3_model_fashion_word_nonword_z <- p3_model_fashion_word_nonword$coefficients[2, 'Robust z']
+p3_model_fashion_word_nonword_p <- (1 - pnorm(abs(p3_model_fashion_word_nonword_z))) * 2
+
+lpp_model_fashion_word_nonword <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "lpp" & category == "fashion" & electrode == "Pz",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+lpp_model_fashion_word_nonword_beta <- lpp_model_fashion_word_nonword$coefficients[2, 'Estimate']
+lpp_model_fashion_word_nonword_se <- lpp_model_fashion_word_nonword$coefficients[2, 'Robust S.E.']
+lpp_model_fashion_word_nonword_z <- lpp_model_fashion_word_nonword$coefficients[2, 'Robust z']
+lpp_model_fashion_word_nonword_p <- (1 - pnorm(abs(lpp_model_fashion_word_nonword_z))) * 2
+
+```
+
+In the fashion condition, words elicited a more positive ERP only in the P2 window ($\beta$ = `r p2_model_fashion_word_nonword_beta %>% round(3)`, *SE* = `r p2_model_fashion_word_nonword_se %>% round(3)`, *z* = `r p2_model_fashion_word_nonword_z %>% round(3)`, *p* = `r p2_model_fashion_word_nonword_p %>% format(scientific=FALSE)`).
+There was no significant difference in the N2 window ($\beta$ = `r n2_model_fashion_word_nonword_beta %>% round(3)`, *SE* = `r n2_model_fashion_word_nonword_se %>% round(3)`, *z* = `r n2_model_fashion_word_nonword_z %>% round(3)`, *p* = `r n2_model_fashion_word_nonword_p %>% format(scientific=FALSE)`), P3 window ($\beta$ = `r p3_model_fashion_word_nonword_beta %>% round(3)`, *SE* = `r p3_model_fashion_word_nonword_se %>% round(3)`, *z* = `r p3_model_fashion_word_nonword_z %>% round(3)`, *p* = `r p3_model_fashion_word_nonword_p %>% format(scientific=FALSE)`), and LPP window ($\beta$ = `r lpp_model_fashion_word_nonword_beta %>% round(3)`, *SE* = `r lpp_model_fashion_word_nonword_se %>% round(3)`, *z* = `r lpp_model_fashion_word_nonword_z %>% round(3)`, *p* = `r lpp_model_fashion_word_nonword_p %>% format(scientific=FALSE)`).
+
+### Pop-out effects
+
+Also following Gantman and Van Bavel, we looked for ERP differences related to the category vs. non-category distinction in all four time windows at electrode Cz.
+
+```{r}
+#| label: Run GEE models for all time windows, moral data pop-out
+#| include: false
+
+p2_model_moral_popout <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "p2" & category == "moral" & is_word == TRUE & electrode == "Cz",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p2_model_moral_popout_beta <- p2_model_moral_popout$coefficients[2, 'Estimate']
+p2_model_moral_popout_se <- p2_model_moral_popout$coefficients[2, 'Robust S.E.']
+p2_model_moral_popout_z <- p2_model_moral_popout$coefficients[2, 'Robust z']
+p2_model_moral_popout_p <- (1 - pnorm(abs(p2_model_moral_popout_z))) * 2
+
+n2_model_moral_popout <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "n2" & category == "moral" & is_word == TRUE & electrode == "Cz",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+n2_model_moral_popout_beta <- n2_model_moral_popout$coefficients[2, 'Estimate']
+n2_model_moral_popout_se <- n2_model_moral_popout$coefficients[2, 'Robust S.E.']
+n2_model_moral_popout_z <- n2_model_moral_popout$coefficients[2, 'Robust z']
+n2_model_moral_popout_p <- (1 - pnorm(abs(n2_model_moral_popout_z))) * 2
+
+p3_model_moral_popout <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "p3" & category == "moral"& is_word == TRUE & electrode == "Cz",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p3_model_moral_popout_beta <- p3_model_moral_popout$coefficients[2, 'Estimate']
+p3_model_moral_popout_se <- p3_model_moral_popout$coefficients[2, 'Robust S.E.']
+p3_model_moral_popout_z <- p3_model_moral_popout$coefficients[2, 'Robust z']
+p3_model_moral_popout_p <- (1 - pnorm(abs(p3_model_moral_popout_z))) * 2
+
+lpp_model_moral_popout <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "lpp" & category == "moral"& is_word == TRUE & electrode == "Cz",
+    data = time_window_data,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+lpp_model_moral_popout_beta <- lpp_model_moral_popout$coefficients[2, 'Estimate']
+lpp_model_moral_popout_se <- lpp_model_moral_popout$coefficients[2, 'Robust S.E.']
+lpp_model_moral_popout_z <- lpp_model_moral_popout$coefficients[2, 'Robust z']
+lpp_model_moral_popout_p <- (1 - pnorm(abs(lpp_model_moral_popout_z))) * 2
+
+```
+
+In the moral condition, there was a significant difference between moral and non-moral words in the P2 window ($\beta$ = `r p2_model_moral_popout_beta %>% round(3)`, *SE* = `r p2_model_moral_popout_se %>% round(3)`, *z* = `r p2_model_moral_popout_z %>% round(3)`, *p* = `r p2_model_moral_popout_p %>% format(scientific=FALSE)`) and the LPP window ($\beta$ = `r lpp_model_moral_popout_beta %>% round(3)`, *SE* = `r lpp_model_moral_popout_se %>% round(3)`, *z* = `r lpp_model_moral_popout_z %>% round(3)`, *p* = `r lpp_model_moral_popout_p %>% format(scientific=FALSE)`).
+However, in both of these cases the effect was in the *opposite* direction as the original, with non-moral words having a more positive ERP.
+There was no significant difference between moral and non-moral words in the N2 window ($\beta$ = `r n2_model_moral_popout_beta %>% round(3)`, *SE* = `r n2_model_moral_popout_se %>% round(3)`, *z* = `r n2_model_moral_popout_z %>% round(3)`, *p* = `r n2_model_moral_popout_p %>% format(scientific=FALSE)`) and P3 window ($\beta$ = `r p3_model_moral_popout_beta %>% round(3)`, *SE* = `r p3_model_moral_popout_se %>% round(3)`, *z* = `r p3_model_moral_popout_z %>% round(3)`, *p* = `r p3_model_moral_popout_p %>% format(scientific=FALSE)`).
+
 ```{r}
@@
 
-p2_model <- gee(v ~ word_category,
+p2_model_fashion_popout <- gee(v ~ word_category,
     id = subject,
@@
 
-p2_model$coefficients
+p2_model_fashion_popout_beta <- p2_model_fashion_popout$coefficients[2, 'Estimate']
+p2_model_fashion_popout_se <- p2_model_fashion_popout$coefficients[2, 'Robust S.E.']
+p2_model_fashion_popout_z <- p2_model_fashion_popout$coefficients[2, 'Robust z']
+p2_model_fashion_popout_p <- (1 - pnorm(abs(p2_model_fashion_popout_z))) * 2
 
-n2_model <- gee(v ~ word_category,
+n2_model_fashion_popout <- gee(v ~ word_category,
     id = subject,
@@
 
-n2_model$coefficients
+n2_model_fashion_popout_beta <- n2_model_fashion_popout$coefficients[2, 'Estimate']
+n2_model_fashion_popout_se <- n2_model_fashion_popout$coefficients[2, 'Robust S.E.']
+n2_model_fashion_popout_z <- n2_model_fashion_popout$coefficients[2, 'Robust z']
+n2_model_fashion_popout_p <- (1 - pnorm(abs(n2_model_fashion_popout_z))) * 2
 
-p3_model <- gee(v ~ word_category,
+p3_model_fashion_popout <- gee(v ~ word_category,
     id = subject,
@@
 
-p3_model$coefficients
+p3_model_fashion_popout_beta <- p3_model_fashion_popout$coefficients[2, 'Estimate']
+p3_model_fashion_popout_se <- p3_model_fashion_popout$coefficients[2, 'Robust S.E.']
+p3_model_fashion_popout_z <- p3_model_fashion_popout$coefficients[2, 'Robust z']
+p3_model_fashion_popout_p <- (1 - pnorm(abs(p3_model_fashion_popout_z))) * 2
 
-lpp_model <- gee(v ~ word_category,
+lpp_model_fashion_popout <- gee(v ~ word_category,
     id = subject,
@@
 
-lpp_model$coefficients
-```
-```{r}
-#| label: Run GEE models for all time windows, moral data pop-out
-#| include: false
-
-p2_model <- gee(v ~ word_category,
-    id = subject,
-    subset = erp_component == "p2" & category == "moral" & is_word == TRUE & electrode == "Cz",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-p2_model$coefficients
-
-n2_model <- gee(v ~ word_category,
-    id = subject,
-    subset = erp_component == "n2" & category == "moral" & is_word == TRUE & electrode == "Cz",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-n2_model$coefficients
-
-p3_model <- gee(v ~ word_category,
-    id = subject,
-    subset = erp_component == "p3" & category == "moral"& is_word == TRUE & electrode == "Cz",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-p3_model$coefficients
-
-lpp_model <- gee(v ~ word_category,
-    id = subject,
-    subset = erp_component == "lpp" & category == "moral"& is_word == TRUE & electrode == "Cz",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-lpp_model$coefficients
-```
-
-```{r}
-#| label: Run GEE models for all time windows, moral data word non-word
-#| include: false
-
-p2_model <- gee(v ~ is_word,
-    id = subject,
-    subset = erp_component == "p2" & category == "moral",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-p2_model$coefficients
-
-n2_model <- gee(v ~ is_word,
-    id = subject,
-    subset = erp_component == "n2" & category == "moral",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-n2_model$coefficients
-
-p3_model <- gee(v ~ is_word,
-    id = subject,
-    subset = erp_component == "p3" & category == "moral",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-p3_model$coefficients
-
-lpp_model <- gee(v ~ is_word,
-    id = subject,
-    subset = erp_component == "lpp" & category == "moral",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-lpp_model$coefficients
+lpp_model_fashion_popout_beta <- lpp_model_fashion_popout$coefficients[2, 'Estimate']
+lpp_model_fashion_popout_se <- lpp_model_fashion_popout$coefficients[2, 'Robust S.E.']
+lpp_model_fashion_popout_z <- lpp_model_fashion_popout$coefficients[2, 'Robust z']
+lpp_model_fashion_popout_p <- (1 - pnorm(abs(lpp_model_fashion_popout_z))) * 2
 
@@
 
-```{r}
-#| label: Run GEE models for all time windows, fashion data word non-word
-#| include: false
-
-p2_model <- gee(v ~ is_word,
-    id = subject,
-    subset = erp_component == "p2" & category == "fashion",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-p2_model$coefficients
-
-n2_model <- gee(v ~ is_word,
-    id = subject,
-    subset = erp_component == "n2" & category == "fashion",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-n2_model$coefficients
-
-p3_model <- gee(v ~ is_word,
-    id = subject,
-    subset = erp_component == "p3" & category == "fashion",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-p3_model$coefficients
-
-lpp_model <- gee(v ~ is_word,
-    id = subject,
-    subset = erp_component == "lpp" & category == "fashion",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-lpp_model$coefficients
-
-```
+In the fashion condition, there was a significant difference in the ERP for fashion and non-fashion words in the effect in the P3 window ($\beta$ = `r p3_model_fashion_popout_beta %>% round(3)`, *SE* = `r p3_model_fashion_popout_se %>% round(3)`, *z* = `r p3_model_fashion_popout_z %>% round(3)`, *p* = `r p3_model_fashion_popout_p %>% format(scientific=FALSE)`).
+There was no significant difference in the P2 window, ($\beta$ = `r p2_model_fashion_popout_beta %>% round(3)`, *SE* = `r p2_model_fashion_popout_se %>% round(3)`, *z* = `r p2_model_fashion_popout_z %>% round(3)`, *p* = `r p2_model_fashion_popout_p %>% format(scientific=FALSE)`), N2 window ($\beta$ = `r n2_model_fashion_popout_beta %>% round(3)`, *SE* = `r n2_model_fashion_popout_se %>% round(3)`, *z* = `r n2_model_fashion_popout_z %>% round(3)`, *p* = `r n2_model_fashion_popout_p %>% format(scientific=FALSE)`), and LPP window ($\beta$ = `r lpp_model_fashion_popout_beta %>% round(3)`, *SE* = `r lpp_model_fashion_popout_se %>% round(3)`, *z* = `r lpp_model_fashion_popout_z %>% round(3)`, *p* = `r lpp_model_fashion_popout_p %>% format(scientific=FALSE)`).

### 2024-03-15 preprocessing/merge-behavioral-local.R

@@ -1,9 +1,20 @@
 library(jsonlite)
 library(dplyr)
 library(readr)
+library(tidyr)
 
 behavior.files <- list.files('data/raw/beh', pattern="json", full.names = T)
 
 merged.data <- lapply(behavior.files, fromJSON) %>% bind_rows()
+
+response_column <- merged.data$response
+
+null_positions <- which(sapply(response_column, is.null))
+
+new_values <- rep(NA, length(response_column))
+
+new_values[-null_positions] <- unlist(response_column, use.names = F)
+
+merged.data$response <- new_values
 
 write_csv(merged.data, file="data/final/behavioral.csv")

### 2024-03-15 manuscript.qmd
fix wording in fashion popout results

@@
 
-In the fashion condition, there was a significant difference in the ERP for fashion and non-fashion words in the effect in the P3 window ($\beta$ = `r p3_model_fashion_popout_beta %>% round(3)`, *SE* = `r p3_model_fashion_popout_se %>% round(3)`, *z* = `r p3_model_fashion_popout_z %>% round(3)`, *p* = `r p3_model_fashion_popout_p %>% format(scientific=FALSE)`).
+In the fashion condition, there fashion words elicited a more positive ERP than non-fashion words in the P3 window ($\beta$ = `r p3_model_fashion_popout_beta %>% round(3)`, *SE* = `r p3_model_fashion_popout_se %>% round(3)`, *z* = `r p3_model_fashion_popout_z %>% round(3)`, *p* = `r p3_model_fashion_popout_p %>% format(scientific=FALSE)`).
 There was no significant difference in the P2 window, ($\beta$ = `r p2_model_fashion_popout_beta %>% round(3)`, *SE* = `r p2_model_fashion_popout_se %>% round(3)`, *z* = `r p2_model_fashion_popout_z %>% round(3)`, *p* = `r p2_model_fashion_popout_p %>% format(scientific=FALSE)`), N2 window ($\beta$ = `r n2_model_fashion_popout_beta %>% round(3)`, *SE* = `r n2_model_fashion_popout_se %>% round(3)`, *z* = `r n2_model_fashion_popout_z %>% round(3)`, *p* = `r n2_model_fashion_popout_p %>% format(scientific=FALSE)`), and LPP window ($\beta$ = `r lpp_model_fashion_popout_beta %>% round(3)`, *SE* = `r lpp_model_fashion_popout_se %>% round(3)`, *z* = `r lpp_model_fashion_popout_z %>% round(3)`, *p* = `r lpp_model_fashion_popout_p %>% format(scientific=FALSE)`).

### 2024-03-18 manuscript.qmd
update based on Jan's comments

@@
 ```{r}
+#| label: Exclude very poor EEG recordings
+#| include: false
+
+exclude_for_eeg_quality <- c("34")
+```
+
+```{r}
 #| label: Flip responses for subject 01, 36 moral words
@@
 
-excluded_subjects <- c(exclude_for_fashion_twice_subjects, exclude_for_non_response_subjects, exclude_for_non_word_response_subjects)
+excluded_subjects <- c(exclude_for_fashion_twice_subjects, exclude_for_non_response_subjects, exclude_for_non_word_response_subjects, exclude_for_eeg_quality)
 
@@
 After applying the exclusion criteria, `r n_subjects_remaining` subjects remain.
-`r length(exclude_for_fashion_twice_subjects)` subjects were excluded for receiving fashion words twice due to a technical error, `r length(exclude_for_non_response_subjects)` subjects were excluded for having a non-response rate greater than 50%, and `r length(exclude_for_non_word_response_subjects)` subjects were excluded for having a non-word response rate greater than 90%.
+`r length(exclude_for_fashion_twice_subjects)` subjects were excluded for receiving fashion words twice due to a technical error, `r length(exclude_for_eeg_quality)` subjects were excluded for having poor EEG recordings, `r length(exclude_for_non_response_subjects)` subjects were excluded for having a non-response rate greater than 50%, and `r length(exclude_for_non_word_response_subjects)` subjects were excluded for having a non-word response rate greater than 90%.
 
@@
 
-We found a pop-out effect for both moral and fashion words.
+We found a pop-out effect fashion words, but not moral words.
+
 In the moral condition, participants were `r mean_moral_in_category`% accurate for moral words and `r mean_moral_out_category`% accurate for non-moral words.
-This difference was statistically significant in the GEE model, $\beta$ = `r coefficient_moral_pop_out %>% round(3)`, *SE* = `r coefficient_moral_pop_out_se %>% round(3)`, *z* = `r z_moral_pop_out %>% round(3)`, *p* = `r p_moral_pop_out %>% format(scientific=FALSE)`.
+This difference was not statistically significant in the GEE model, $\beta$ = `r coefficient_moral_pop_out %>% round(3)`, *SE* = `r coefficient_moral_pop_out_se %>% round(3)`, *z* = `r z_moral_pop_out %>% round(3)`, *p* = `r p_moral_pop_out %>% format(scientific=FALSE)`.
 
@@
 eeg_data <- read_csv("data/final/eeg.csv", col_types = "cdcllcdc") %>%
-  filter(!subject %in% excluded_subjects) %>%
-  filter(subject != "34") # really few usable segments
+  filter(!subject %in% excluded_subjects)
 ```
@@
 ```{r}
-#| label: Flip subject 01s responses
+#| label: Flip subject 01s, 1/2 36s responses
 #| include: false
@@
 #| fig-height: 8
-#| fig-cap: Grand average waveforms. Shaded areas represent +/- 1 SE.
+#| fig-cap: Grand average waveforms. Shaded areas represent +/- 1 SE. Dotted vertical lines represent the time windows of interest.
 #| echo: false
@@
   geom_vline(xintercept = 0)+
+  geom_vline(xintercept = c(200, 250, 350, 600, 800), linetype="dotted", alpha=0.6)+
   geom_ribbon(aes(ymin=M-SE, ymax=M+SE, fill=is_word), alpha=0.2, color=NA)+

### 2024-03-20 manuscript.qmd
begin work on phase 2 data collection integration

@@
 
-behavioral_data <- read_csv('data/final/behavioral.csv')
+behavioral_data <- read_csv('data/phase_2/final/behavioral.csv')
 ```
@@
 
-eeg_data <- read_csv("data/final/eeg.csv", col_types = "cdcllcdc") %>%
+eeg_data <- read_csv("data/phase_2/final/eeg.csv", col_types = "cdcllcdc") %>%
   filter(!subject %in% excluded_subjects)

### 2024-03-20 preprocessing/mege-local.R

@@ -3,7 +3,9 @@ library(dplyr)
 
 # Read in all CSVs in the data/preprocessed directory
 
-files <- list.files("data/preprocessed", pattern = "*.csv", full.names = TRUE)
+which_phase <- "phase_2"
+
+files <- list.files(paste0("data/", which_phase, "/preprocessed"), pattern = "*.csv", full.names = TRUE)
 data <- lapply(files, function(x){
   read_csv(x, col_types = "cdcllcddlc") %>% 
     dplyr::filter(electrode %in% c("Cz", "Pz")) %>%
@@ -11,4 +13,4 @@ data <- lapply(files, function(x){
 }) %>% 
   bind_rows()
 
-write_csv(data, "data/final/eeg.csv")
+write_csv(data, paste0("data/", which_phase, "/final/eeg.csv"))

### 2024-03-20 preprocessing/merge-behavioral-local.R

@@ -3,7 +3,11 @@ library(dplyr)
 library(readr)
 library(tidyr)
 
-behavior.files <- list.files('data/raw/beh', pattern="json", full.names = T)
+
+which_phase <- "phase_2"
+
+
+behavior.files <- list.files(paste0('data/', which_phase, '/raw/beh'), pattern="json", full.names = T)
 
 merged.data <- lapply(behavior.files, fromJSON) %>% bind_rows()
 
@@ -17,4 +21,4 @@ new_values[-null_positions] <- unlist(response_column, use.names = F)
 
 merged.data$response <- new_values
 
-write_csv(merged.data, file="data/final/behavioral.csv")
+write_csv(merged.data, file=paste0("data/", which_phase, "/final/behavioral.csv"))

### 2024-03-20 preprocessing/run_preprocessing_local_machine.R

@@ -2,21 +2,23 @@ library(readr)
 library(stringr)
 source("preprocessing/preprocessing-eeg-functions.R")
 
-subjects <- list.files('data/raw/beh/', pattern="json") %>% 
+which_phase <- "phase_2"
+
+subjects <- list.files(paste0('data/', which_phase, '/raw/beh/'), pattern="json") %>% 
   str_extract("[0-9]*.json") %>%
   str_remove(".json")
 
 for(subject in subjects){
   
-  final.path <- paste0("data/preprocessed/subject-", subject,"-epochs.csv")
+  final.path <- paste0("data/", which_phase, "/preprocessed/subject-", subject,"-epochs.csv")
   print(paste0("Working on ",subject))
   if(file.exists(final.path)){
     print(paste0("epochs.csv already exists - skipping"))
     next
   }
   tryCatch({
-    eeg.file <- list.files('data/raw/eeg', pattern=paste0("subject-", subject), full.names = T)
-    beh.file <- paste0('data/raw/beh/219_2024_behavioral_', subject,'.json')
+    eeg.file <- list.files(paste0('data/', which_phase, '/raw/eeg'), pattern=paste0("subject-", subject), full.names = T)
+    beh.file <- paste0('data/', which_phase, '/raw/beh/219_2024_', if_else(which_phase=="phase_2", "v2_", ""), 'behavioral_', subject,'.json')
     
     preprocessed.data <- preprocess_eeg(
       file = eeg.file, 
@@ -34,7 +36,7 @@ for(subject in subjects){
       eye_threshold = 70,
       which_electrodes = c("Fp1", "Fp2", "Cz", "Pz"))
     
-    write_csv(preprocessed.data, file=paste0("data/preprocessed/subject-", subject,"-epochs.csv"))
+    write_csv(preprocessed.data, file=paste0("data/", which_phase, "/preprocessed/subject-", subject,"-epochs.csv"))
   },
   error = function(cond){
     message(cond)

### 2024-03-20 preprocessing/download-raw-data-from-osf.R
update for phase 2

@@ -8,3 +8,14 @@ osf_retrieve_node("v7mbj") %>%
 osf_retrieve_node("v7mbj") %>%
   osf_ls_files(path="EEG", n_max=Inf) %>%
   osf_download(path="data/raw/eeg", conflicts="skip")
+
+
+# phase 2
+
+osf_retrieve_node("gd24h") %>%
+  osf_ls_files(path="Behavioral", n_max=Inf) %>%
+  osf_download(path="data/phase_2/raw/beh", conflicts="skip")
+
+osf_retrieve_node("gd24h") %>%
+  osf_ls_files(path="EEG", n_max=Inf) %>%
+  osf_download(path="data/phase_2/raw/eeg", conflicts="skip")

### 2024-03-21 manuscript.qmd
include study 2 in quarto doc

@@
 
-# Methods
+## Experiment 1
+
+### Methods
+
+```{r}
+#| label: Download study 1 data from the OSF
+#| include: false
+osf_retrieve_node("ngtha") %>%
+  osf_ls_files() %>%
+  osf_download(path="data/phase_1/final", conflicts="skip")
+```
+
+```{r}
+#| label: Load the study 1 behavioral data
+#| include: false
+
+behavioral_data_study_1 <- read_csv('data/phase_1/final/behavioral.csv')
+```
+
+#### Participants
+
+```{r}
+#| label: Filter out the study 1 subjects who got fashion words twice due to programming error
+#| include: false
+
+exclude_for_fashion_twice_subjects_study_1 <- behavioral_data_study_1 %>%
+  filter(phase == "fashion", task == "response") %>%
+  group_by(subject_id) %>%
+  count() %>%
+  filter(n == 600) %>%
+  pull(subject_id)
+```
+
+```{r}
+#| label: Exclude very poor EEG recordings for study 1
+#| include: false
+
+exclude_for_eeg_quality_study_1 <- c("34")
+```
+
+```{r}
+#| label: Flip responses for study 1 subject 01, 36 moral words
+#| include: false
+
+behavioral_data_key_corrected_study_1 <- behavioral_data_study_1 %>%
+  mutate(correct = ifelse(subject_id == "01", !correct, correct)) %>%
+  mutate(correct = ifelse(subject_id == "36" & phase == "moral", !correct, correct))
+```
+
+```{r}
+#| label: Get study 1 subject non-response rate
+#| include: false
+
+subject_non_response_rate_study_1 <- behavioral_data_key_corrected_study_1 %>%
+  filter(phase == "moral" | phase == "fashion") %>%
+  filter(task == "response") %>%
+  group_by(subject_id) %>%
+  summarise(non_response_rate = mean(is.na(rt)))
+
+exclude_for_non_response_subjects_study_1 <- subject_non_response_rate_study_1 %>%
+  filter(non_response_rate > 0.5) %>%
+  pull(subject_id)
+```
+
+```{r}
+#| label: Compute study 1 subject non-word response rate
+#| include: false
+
+subject_non_word_response_rate_study_1 <- behavioral_data_key_corrected_study_1 %>%
+  filter(phase == "moral" | phase == "fashion") %>%
+  filter(task == "response") %>%
+  group_by(subject_id) %>%
+  mutate(non_word_response = ifelse(
+    (is_word == FALSE & correct == TRUE) |
+    (is_word == TRUE & correct == FALSE), 1, 0)) %>%
+  summarize(non_word_response_rate = mean(non_word_response))
+
+exclude_for_non_word_response_subjects_study_1 <- subject_non_word_response_rate_study_1 %>%
+  filter(non_word_response_rate > 0.9) %>%
+  pull(subject_id)
+```
+
+```{r}
+#| label: Create study 1 filtered data set by applying exclusions
+#| include: false
+
+excluded_subjects_study_1 <- c(
+  exclude_for_fashion_twice_subjects_study_1, 
+  exclude_for_non_response_subjects_study_1, 
+  exclude_for_non_word_response_subjects_study_1, 
+  exclude_for_eeg_quality_study_1
+)
+
+behavioral_data_filtered_study_1 <- behavioral_data_key_corrected_study_1 %>%
+  filter(!subject_id %in% excluded_subjects_study_1)
+```
+
+```{r}
+#| label: Count the number of study 1 subjects and subjects remaining
+#| include: false
+
+n_subjects_study_1 <- behavioral_data_study_1 %>% pull(subject_id) %>% unique() %>% length()
+
+n_subjects_remaining_study_1 <- behavioral_data_filtered_study_1 %>% pull(subject_id) %>% unique() %>% length()
+```
+
+`r n_subjects_study_1` subjects participated in the study.
+After applying the exclusion criteria, `r n_subjects_remaining_study_1` subjects remain.
+`r length(exclude_for_fashion_twice_subjects_study_1)` subjects were excluded for receiving fashion words twice due to a technical error, `r length(exclude_for_eeg_quality_study_1)` subjects were excluded for having poor EEG recordings, `r length(exclude_for_non_response_subjects_study_1)` subjects were excluded for having a non-response rate greater than 50%, and `r length(exclude_for_non_word_response_subjects_study_1)` subjects were excluded for having a non-word response rate greater than 90%.
+
+### Results
+
+#### Behavioral
+
+```{r}
+#| label: Select relevant study 1 behavioral test data
+#| include: false
+
+behavioral_data_test_set_study_1 <- behavioral_data_filtered_study_1 %>%
+  filter(phase == "moral" | phase == "fashion") %>%
+  filter(task == "response") %>%
+  select(subject_id, word_type, is_word, correct, rt) %>%
+  mutate(word_category = ifelse(word_type %in% c("fashion", "moral"), "category", "non-category"),
+         category = ifelse(word_type %in% c("fashion", "non-fashion"), "fashion", "moral"))
+```
+
+```{r}
+#| label: Compute study 1 accuracy
+#| include: false
+
+subject_level_accuracy_study_1 <- behavioral_data_test_set_study_1 %>%
+  group_by(subject_id, word_category, category, is_word) %>%
+  summarise(accuracy = mean(correct), se=sd(correct)/sqrt(n()))
+```
+
+```{r}
+#| label: fig-beh-pop-out-study-1
+#| fig-cap: Performance for in-category words and out-of-category words for each participant.
+Points above the diagonal represent higher accuracy for in-category words.
+Overall accuracy was much higher than expected.
+We later discovered this was due to a difference in procedure between our study and the original study.
+Lines represent +/- 1 SE.
+#| echo: false
+
+behavioral_pop_out_data_study_1 <- subject_level_accuracy_study_1 %>%
+  filter(is_word == TRUE) %>%
+  pivot_wider(names_from = word_category, values_from = c(accuracy, se))
+
+ggplot(behavioral_pop_out_data_study_1, aes(x=`accuracy_non-category`, y=`accuracy_category`))+
+  geom_point()+
+  geom_linerange(aes(ymin=`accuracy_category`-`se_category`, ymax=`accuracy_category`+`se_category`), linewidth=0.25)+
+  geom_linerange(aes(xmin=`accuracy_non-category`-`se_non-category`, xmax=`accuracy_non-category`+`se_non-category`), linewidth=0.25, alpha=0.3)+
+  labs(x="Accuracy for non-category words", y="Accuracy for category words")+
+  facet_grid(.~category, labeller = as_labeller(c("fashion"="Fashion Words", "moral"="Moral Words")))+ 
+  geom_abline(intercept = 0, slope = 1, linetype="dashed")+
+  coord_cartesian(xlim=c(0.5,1), ylim=c(0.5,1))+
+  theme_bw(base_size=12)+
+  theme(aspect.ratio=1, panel.grid=element_blank())
+```
+
+```{r}
+#| label: GEE models for study 1 pop out effects
+#| include: false
+
+behavioral_model_moral_pop_out_study_1 <- gee(correct ~ word_category,
+    id = subject_id,
+    subset = is_word == TRUE & category == "moral",
+    data = behavioral_data_test_set_study_1,
+    family = binomial,
+    corstr = "exchangeable") %>% summary()
+
+coefficient_moral_pop_out_study_1 <- behavioral_model_moral_pop_out_study_1$coefficients[2, 'Estimate']
+coefficient_moral_pop_out_se_study_1 <- behavioral_model_moral_pop_out_study_1$coefficients[2, 'Robust S.E.']
+z_moral_pop_out_study_1 <- behavioral_model_moral_pop_out_study_1$coefficients[2, 'Robust z']
+p_moral_pop_out_study_1 <- (1 - pnorm(abs(z_moral_pop_out_study_1))) * 2
+
+fashion_model_moral_pop_out_study_1 <- gee(correct ~ word_category,
+    id = subject_id,
+    subset = is_word == TRUE & category == "fashion",
+    data = behavioral_data_test_set_study_1,
+    family = binomial,
+    corstr = "exchangeable") %>% summary()
+
+coefficient_fashion_pop_out_study_1 <- fashion_model_moral_pop_out_study_1$coefficients[2, 'Estimate']
+coefficient_fashion_pop_out_se_study_1 <- fashion_model_moral_pop_out_study_1$coefficients[2, 'Robust S.E.']
+z_fashion_pop_out_study_1 <- fashion_model_moral_pop_out_study_1$coefficients[2, 'Robust z']
+p_fashion_pop_out_study_1 <- (1 - pnorm(abs(z_fashion_pop_out_study_1))) * 2
+
+mean_moral_in_category_study_1 <- subject_level_accuracy_study_1 %>%
+  filter(is_word == TRUE & category == "moral" & word_category == "category") %>%
+  pull(accuracy) %>%
+  mean() %>% 
+  round(4)* 100
+
+mean_moral_out_category_study_1 <- subject_level_accuracy_study_1 %>%
+  filter(is_word == TRUE & category == "moral" & word_category == "non-category") %>%
+  pull(accuracy) %>%
+  mean() %>% 
+  round(4)* 100
+
+mean_fashion_in_category_study_1 <- subject_level_accuracy_study_1 %>%
+  filter(is_word == TRUE & category == "fashion" & word_category == "category") %>%
+  pull(accuracy) %>%
+  mean() %>% 
+  round(4)* 100
+
+mean_fashion_out_category_study_1 <- subject_level_accuracy_study_1 %>%
+  filter(is_word == TRUE & category == "fashion" & word_category == "non-category") %>%
+  pull(accuracy) %>%
+  mean() %>% 
+  round(4)* 100
+```
+
+We found a pop-out effect fashion words, but not moral words.
+
+In the moral condition, participants were `r mean_moral_in_category_study_1`% accurate for moral words and `r mean_moral_out_category_study_1`% accurate for non-moral words.
+This difference was not statistically significant in the GEE model, $\beta$ = `r coefficient_moral_pop_out_study_1 %>% round(3)`, *SE* = `r coefficient_moral_pop_out_se_study_1 %>% round(3)`, *z* = `r z_moral_pop_out_study_1 %>% round(3)`, *p* = `r p_moral_pop_out_study_1 %>% format(scientific=FALSE)`.
+
+In the fashion condition, participants were `r mean_fashion_in_category_study_1`% accurate for fashion words and `r mean_fashion_out_category_study_1`% accurate for non-fashion words.
+This difference was statistically significant in the GEE model, $\beta$ = `r coefficient_fashion_pop_out_study_1`, *SE* = `r coefficient_fashion_pop_out_se_study_1 %>% round(3)`, *z* = `r z_fashion_pop_out_study_1 %>% round(3)`, *p* = `r p_fashion_pop_out_study_1 %>% format(scientific=FALSE)`.
+
+#### EEG
+
+```{r}
+#| label: Load study 1 eeg data
+#| include: false
+
+eeg_data_study_1 <- read_csv("data/phase_1/final/eeg.csv", col_types = "cdcllcdc") %>%
+  filter(!subject %in% excluded_subjects_study_1)
+```
+
+```{r}
+#| label: Flip study 1 subject 01s, 1/2 36s responses
+#| include: false
+
+eeg_data_key_corrected_study_1 <- eeg_data_study_1 %>%
+  mutate(correct = ifelse(subject == "01", !correct, correct)) %>%
+  mutate(correct = ifelse(subject == "36" & word_type == "moral", !correct, correct))
+```
+
+```{r}
+#| label: Compute study 1 subject ERPs
+#| include: false
+
+subject_eeg_study_1 <- eeg_data_key_corrected_study_1 %>%
+  filter(electrode %in% c("Cz", "Pz")) %>%
+  filter(correct == TRUE) %>%
+  group_by(subject, t, electrode, word_type, is_word) %>%
+  summarize(v = mean(v), n=n()) %>%
+  mutate(word_category = ifelse(word_type %in% c("fashion", "moral"), "category", "non-category"),
+         category = ifelse(word_type %in% c("fashion", "non-fashion"), "fashion", "moral"))
+```
+
+```{r}
+#| label: Compute study 1 grand average
+#| include: false
+
+grand_average_study_1 <- subject_eeg_study_1 %>%
+  group_by(t, electrode, word_category, category, is_word) %>%
+  summarize(M = mean(v), SE = sd(v)/sqrt(n()))
+```
+
+```{r}
+#| label: fig-grand-averages-study-1
+#| fig-width: 10
+#| fig-height: 8
+#| fig-cap: Grand average waveforms. Shaded areas represent +/- 1 SE. Dotted vertical lines represent the time windows of interest.
+#| echo: false
+
+ggplot(grand_average_study_1, aes(x=t, y=M, color=is_word, linetype=word_category)) +
+  geom_hline(yintercept = 0)+
+  geom_vline(xintercept = 0)+
+  geom_vline(xintercept = c(200, 250, 350, 600, 800), linetype="dotted", alpha=0.6)+
+  geom_ribbon(aes(ymin=M-SE, ymax=M+SE, fill=is_word), alpha=0.2, color=NA)+
+  geom_line()+
+  scale_x_continuous(breaks=c(0,500, 1000))+
+  scale_color_brewer(palette="Set1", name="Is word?", labels=c("Non-word", "Word"))+
+  scale_fill_brewer(palette="Set1", name="Is word?", labels=c("Non-word", "Word"))+
+  scale_linetype_manual(name="Word Category", labels=c("Moral/Fashion", "Non-Moral/Non-Fashion"), values=c("solid", "dashed"))+
+  facet_grid(electrode~category, labeller=as_labeller(c("fashion"="Fashion Words", "moral"="Moral Words", "Cz"="Cz", "Pz"="Pz" )))+
+  labs(x="Time since word onset (ms)", y="Voltage (uV)", color="Is word?", fill="Is word?", linetype="Word Category")+
+  theme_minimal(base_size=12)+
+  theme(panel.grid = element_blank())
+```
+
+```{r}
+#| label: Count the number of study 1 good segments per subject
+#| include: false
+
+count_good_trials_study_1 <- eeg_data_study_1 %>%
+  filter(t==0, electrode=="Cz") %>%
+  group_by(subject) %>%
+  summarize(n=n()) %>%
+  mutate(percent = (n/600)*100)
+
+mean_good_trials_study_1 <- mean(count_good_trials_study_1$n)
+sd_good_trials_study_1 <- sd(count_good_trials_study_1$n)
+
+```
+
+```{r}
+#| label: Define time windows
+#| include: false
+p2.window.start <- 200
+p2.window.end <- 250
+n2.window.start <- 250
+n2.window.end <- 350
+p3.window.start <- 350
+p3.window.end <- 600
+lpp.window.start <- 600
+lpp.window.end <- 800
+
+# vectorized function for indicating time window
+get_time_window <- function(t){
+  ifelse(t >= p2.window.start & t < p2.window.end, "p2",
+  ifelse(t >= n2.window.start & t < n2.window.end, "n2",
+  ifelse(t >= p3.window.start & t < p3.window.end, "p3",
+  ifelse(t >= lpp.window.start & t < lpp.window.end, "lpp",
+  "other"))))
+}
+```
+
+```{r}
+#| label: Calculate mean voltage in all time windows for each trial for study 1
+#| include: false
+
+time_window_data_study_1 <- eeg_data_study_1 %>%
+  filter(electrode %in% c("Cz", "Pz")) %>%
+  filter(correct == TRUE) %>%
+  mutate(erp_component = get_time_window(t)) %>%
+  filter(erp_component != "other") %>%
+  group_by(subject, electrode, word_type, is_word, erp_component) %>%
+  summarize(v = mean(v)) %>%
+  mutate(word_category = ifelse(word_type %in% c("fashion", "moral"), "category", "non-category"),
+         category = ifelse(word_type %in% c("fashion", "non-fashion"), "fashion", "moral"))
+```
+
+##### Words vs. Non-Words
+
+Following Gantman et al. (2020), we looked for word vs. non-word ERP effects at each time window at electrode Pz.
+
+```{r}
+#| label: Run GEE models for all time windows, moral data word non-word, study 1
+#| include: false
+
+p2_model_moral_word_nonword_study_1 <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "p2" & category == "moral" & electrode == "Pz",
+    data = time_window_data_study_1,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p2_model_moral_word_nonword_beta_study_1 <- p2_model_moral_word_nonword_study_1$coefficients[2, 'Estimate']
+p2_model_moral_word_nonword_se_study_1 <- p2_model_moral_word_nonword_study_1$coefficients[2, 'Robust S.E.']
+p2_model_moral_word_nonword_z_study_1 <- p2_model_moral_word_nonword_study_1$coefficients[2, 'Robust z']
+p2_model_moral_word_nonword_p_study_1 <- (1 - pnorm(abs(p2_model_moral_word_nonword_z_study_1))) * 2
+
+n2_model_moral_word_nonword_study_1 <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "n2" & category == "moral" & electrode == "Pz",
+    data = time_window_data_study_1,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+n2_model_moral_word_nonword_beta_study_1 <- n2_model_moral_word_nonword_study_1$coefficients[2, 'Estimate']
+n2_model_moral_word_nonword_se_study_1 <- n2_model_moral_word_nonword_study_1$coefficients[2, 'Robust S.E.']
+n2_model_moral_word_nonword_z_study_1 <- n2_model_moral_word_nonword_study_1$coefficients[2, 'Robust z']
+n2_model_moral_word_nonword_p_study_1 <- (1 - pnorm(abs(n2_model_moral_word_nonword_z_study_1))) * 2
+
+p3_model_moral_word_nonword_study_1 <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "p3" & category == "moral" & electrode == "Pz",
+    data = time_window_data_study_1,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p3_model_moral_word_nonword_beta_study_1 <- p3_model_moral_word_nonword_study_1$coefficients[2, 'Estimate']
+p3_model_moral_word_nonword_se_study_1 <- p3_model_moral_word_nonword_study_1$coefficients[2, 'Robust S.E.']
+p3_model_moral_word_nonword_z_study_1 <- p3_model_moral_word_nonword_study_1$coefficients[2, 'Robust z']
+p3_model_moral_word_nonword_p_study_1 <- (1 - pnorm(abs(p3_model_moral_word_nonword_z_study_1))) * 2
+
+lpp_model_moral_word_nonword_study_1 <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "lpp" & category == "moral" & electrode == "Pz",
+    data = time_window_data_study_1,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+lpp_model_moral_word_nonword_beta_study_1 <- lpp_model_moral_word_nonword_study_1$coefficients[2, 'Estimate']
+lpp_model_moral_word_nonword_se_study_1 <- lpp_model_moral_word_nonword_study_1$coefficients[2, 'Robust S.E.']
+lpp_model_moral_word_nonword_z_study_1 <- lpp_model_moral_word_nonword_study_1$coefficients[2, 'Robust z']
+lpp_model_moral_word_nonword_p_study_1 <- (1 - pnorm(abs(lpp_model_moral_word_nonword_z_study_1))) * 2
+```
+
+In the moral condition, words elicited a more positive ERP in the P2 window ($\beta$ = `r p2_model_moral_word_nonword_beta_study_1 %>% round(3)`, *SE* = `r p2_model_moral_word_nonword_se_study_1 %>% round(3)`, *z* = `r p2_model_moral_word_nonword_z_study_1 %>% round(3)`, *p* = `r p2_model_moral_word_nonword_p_study_1 %>% format(scientific=FALSE)`), N2 window ($\beta$ = `r n2_model_moral_word_nonword_beta_study_1 %>% round(3)`, *SE* = `r n2_model_moral_word_nonword_se_study_1 %>% round(3)`, *z* = `r n2_model_moral_word_nonword_z_study_1 %>% round(3)`, *p* = `r n2_model_moral_word_nonword_p_study_1 %>% format(scientific=FALSE)`), and P3 window ($\beta$ = `r p3_model_moral_word_nonword_beta_study_1 %>% round(3)`, *SE* = `r p3_model_moral_word_nonword_se_study_1 %>% round(3)`, *z* = `r p3_model_moral_word_nonword_z_study_1 %>% round(3)`, *p* = `r p3_model_moral_word_nonword_p_study_1 %>% format(scientific=FALSE)`).
+There was no significant effect in the LPP window ($\beta$ = `r lpp_model_moral_word_nonword_beta_study_1 %>% round(3)`, *SE* = `r lpp_model_moral_word_nonword_se_study_1 %>% round(3)`, *z* = `r lpp_model_moral_word_nonword_z_study_1 %>% round(3)`, *p* = `r lpp_model_moral_word_nonword_p_study_1 %>% format(scientific=FALSE)`).
+
+```{r}
+#| label: Run GEE models for all time windows, fashion data word non-word, study 1
+#| include: false
+
+p2_model_fashion_word_nonword_study_1 <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "p2" & category == "fashion" & electrode == "Pz",
+    data = time_window_data_study_1,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p2_model_fashion_word_nonword_beta_study_1 <- p2_model_fashion_word_nonword_study_1$coefficients[2, 'Estimate']
+p2_model_fashion_word_nonword_se_study_1 <- p2_model_fashion_word_nonword_study_1$coefficients[2, 'Robust S.E.']
+p2_model_fashion_word_nonword_z_study_1 <- p2_model_fashion_word_nonword_study_1$coefficients[2, 'Robust z']
+p2_model_fashion_word_nonword_p_study_1 <- (1 - pnorm(abs(p2_model_fashion_word_nonword_z_study_1))) * 2
+
+n2_model_fashion_word_nonword_study_1 <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "n2" & category == "fashion" & electrode == "Pz",
+    data = time_window_data_study_1,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+n2_model_fashion_word_nonword_beta_study_1 <- n2_model_fashion_word_nonword_study_1$coefficients[2, 'Estimate']
+n2_model_fashion_word_nonword_se_study_1 <- n2_model_fashion_word_nonword_study_1$coefficients[2, 'Robust S.E.']
+n2_model_fashion_word_nonword_z_study_1 <- n2_model_fashion_word_nonword_study_1$coefficients[2, 'Robust z']
+n2_model_fashion_word_nonword_p_study_1 <- (1 - pnorm(abs(n2_model_fashion_word_nonword_z_study_1))) * 2
+
+p3_model_fashion_word_nonword_study_1 <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "p3" & category == "fashion" & electrode == "Pz",
+    data = time_window_data_study_1,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p3_model_fashion_word_nonword_beta_study_1 <- p3_model_fashion_word_nonword_study_1$coefficients[2, 'Estimate']
+p3_model_fashion_word_nonword_se_study_1 <- p3_model_fashion_word_nonword_study_1$coefficients[2, 'Robust S.E.']
+p3_model_fashion_word_nonword_z_study_1 <- p3_model_fashion_word_nonword_study_1$coefficients[2, 'Robust z']
+p3_model_fashion_word_nonword_p_study_1 <- (1 - pnorm(abs(p3_model_fashion_word_nonword_z_study_1))) * 2
+
+lpp_model_fashion_word_nonword_study_1 <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "lpp" & category == "fashion" & electrode == "Pz",
+    data = time_window_data_study_1,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+lpp_model_fashion_word_nonword_beta_study_1 <- lpp_model_fashion_word_nonword_study_1$coefficients[2, 'Estimate']
+lpp_model_fashion_word_nonword_se_study_1 <- lpp_model_fashion_word_nonword_study_1$coefficients[2, 'Robust S.E.']
+lpp_model_fashion_word_nonword_z_study_1 <- lpp_model_fashion_word_nonword_study_1$coefficients[2, 'Robust z']
+lpp_model_fashion_word_nonword_p_study_1 <- (1 - pnorm(abs(lpp_model_fashion_word_nonword_z_study_1))) * 2
+
+```
+
+In the fashion condition, there was no significant difference in any of the time windows; P2 window ($\beta$ = `r p2_model_fashion_word_nonword_beta_study_1 %>% round(3)`, *SE* = `r p2_model_fashion_word_nonword_se_study_1 %>% round(3)`, *z* = `r p2_model_fashion_word_nonword_z_study_1 %>% round(3)`, *p* = `r p2_model_fashion_word_nonword_p_study_1 %>% format(scientific=FALSE)`), N2 window ($\beta$ = `r n2_model_fashion_word_nonword_beta_study_1 %>% round(3)`, *SE* = `r n2_model_fashion_word_nonword_se_study_1 %>% round(3)`, *z* = `r n2_model_fashion_word_nonword_z_study_1 %>% round(3)`, *p* = `r n2_model_fashion_word_nonword_p_study_1 %>% format(scientific=FALSE)`), P3 window ($\beta$ = `r p3_model_fashion_word_nonword_beta_study_1 %>% round(3)`, *SE* = `r p3_model_fashion_word_nonword_se_study_1 %>% round(3)`, *z* = `r p3_model_fashion_word_nonword_z_study_1 %>% round(3)`, *p* = `r p3_model_fashion_word_nonword_p_study_1 %>% format(scientific=FALSE)`), and LPP window ($\beta$ = `r lpp_model_fashion_word_nonword_beta_study_1 %>% round(3)`, *SE* = `r lpp_model_fashion_word_nonword_se_study_1 %>% round(3)`, *z* = `r lpp_model_fashion_word_nonword_z_study_1 %>% round(3)`, *p* = `r lpp_model_fashion_word_nonword_p_study_1 %>% format(scientific=FALSE)`).
+
+##### Pop-out effects
+
+Also following Gantman et al. (2020), we looked for ERP differences related to the category vs. non-category distinction in all four time windows at electrode Cz.
+
+```{r}
+#| label: Run GEE models for all time windows, moral data pop-out, study 1
+#| include: false
+
+p2_model_moral_popout_study_1 <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "p2" & category == "moral" & is_word == TRUE & electrode == "Cz",
+    data = time_window_data_study_1,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p2_model_moral_popout_beta_study_1 <- p2_model_moral_popout_study_1$coefficients[2, 'Estimate']
+p2_model_moral_popout_se_study_1 <- p2_model_moral_popout_study_1$coefficients[2, 'Robust S.E.']
+p2_model_moral_popout_z_study_1 <- p2_model_moral_popout_study_1$coefficients[2, 'Robust z']
+p2_model_moral_popout_p_study_1 <- (1 - pnorm(abs(p2_model_moral_popout_z_study_1))) * 2
+
+n2_model_moral_popout_study_1 <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "n2" & category == "moral" & is_word == TRUE & electrode == "Cz",
+    data = time_window_data_study_1,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+n2_model_moral_popout_beta_study_1 <- n2_model_moral_popout_study_1$coefficients[2, 'Estimate']
+n2_model_moral_popout_se_study_1 <- n2_model_moral_popout_study_1$coefficients[2, 'Robust S.E.']
+n2_model_moral_popout_z_study_1 <- n2_model_moral_popout_study_1$coefficients[2, 'Robust z']
+n2_model_moral_popout_p_study_1 <- (1 - pnorm(abs(n2_model_moral_popout_z_study_1))) * 2
+
+p3_model_moral_popout_study_1 <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "p3" & category == "moral"& is_word == TRUE & electrode == "Cz",
+    data = time_window_data_study_1,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p3_model_moral_popout_beta_study_1 <- p3_model_moral_popout_study_1$coefficients[2, 'Estimate']
+p3_model_moral_popout_se_study_1 <- p3_model_moral_popout_study_1$coefficients[2, 'Robust S.E.']
+p3_model_moral_popout_z_study_1 <- p3_model_moral_popout_study_1$coefficients[2, 'Robust z']
+p3_model_moral_popout_p_study_1 <- (1 - pnorm(abs(p3_model_moral_popout_z_study_1))) * 2
+
+lpp_model_moral_popout_study_1 <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "lpp" & category == "moral"& is_word == TRUE & electrode == "Cz",
+    data = time_window_data_study_1,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+lpp_model_moral_popout_beta_study_1 <- lpp_model_moral_popout_study_1$coefficients[2, 'Estimate']
+lpp_model_moral_popout_se_study_1 <- lpp_model_moral_popout_study_1$coefficients[2, 'Robust S.E.']
+lpp_model_moral_popout_z_study_1 <- lpp_model_moral_popout_study_1$coefficients[2, 'Robust z']
+lpp_model_moral_popout_p_study_1 <- (1 - pnorm(abs(lpp_model_moral_popout_z_study_1))) * 2
+
+```
+
+In the moral condition, there were no significant differences between moral and non-moral words in the P2 window ($\beta$ = `r p2_model_moral_popout_beta_study_1 %>% round(3)`, *SE* = `r p2_model_moral_popout_se_study_1 %>% round(3)`, *z* = `r p2_model_moral_popout_z_study_1 %>% round(3)`, *p* = `r p2_model_moral_popout_p_study_1 %>% format(scientific=FALSE)`), N2 window ($\beta$ = `r n2_model_moral_popout_beta_study_1 %>% round(3)`, *SE* = `r n2_model_moral_popout_se_study_1 %>% round(3)`, *z* = `r n2_model_moral_popout_z_study_1 %>% round(3)`, *p* = `r n2_model_moral_popout_p_study_1 %>% format(scientific=FALSE)`), P3 window ($\beta$ = `r p3_model_moral_popout_beta_study_1 %>% round(3)`, *SE* = `r p3_model_moral_popout_se_study_1 %>% round(3)`, *z* = `r p3_model_moral_popout_z_study_1 %>% round(3)`, *p* = `r p3_model_moral_popout_p_study_1 %>% format(scientific=FALSE)`), and the LPP window ($\beta$ = `r lpp_model_moral_popout_beta_study_1 %>% round(3)`, *SE* = `r lpp_model_moral_popout_se_study_1 %>% round(3)`, *z* = `r lpp_model_moral_popout_z_study_1 %>% round(3)`, *p* = `r lpp_model_moral_popout_p_study_1 %>% format(scientific=FALSE)`).
+
+```{r}
+#| label: Run GEE models for all time windows, fashion data pop-out, study 1
+#| include: false
+
+p2_model_fashion_popout_study_1 <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "p2" & category == "fashion" & is_word == TRUE & electrode == "Cz",
+    data = time_window_data_study_1,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p2_model_fashion_popout_beta_study_1 <- p2_model_fashion_popout_study_1$coefficients[2, 'Estimate']
+p2_model_fashion_popout_se_study_1 <- p2_model_fashion_popout_study_1$coefficients[2, 'Robust S.E.']
+p2_model_fashion_popout_z_study_1 <- p2_model_fashion_popout_study_1$coefficients[2, 'Robust z']
+p2_model_fashion_popout_p_study_1 <- (1 - pnorm(abs(p2_model_fashion_popout_z_study_1))) * 2
+
+n2_model_fashion_popout_study_1 <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "n2" & category == "fashion"& is_word == TRUE & electrode == "Cz",
+    data = time_window_data_study_1,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+n2_model_fashion_popout_beta_study_1 <- n2_model_fashion_popout_study_1$coefficients[2, 'Estimate']
+n2_model_fashion_popout_se_study_1 <- n2_model_fashion_popout_study_1$coefficients[2, 'Robust S.E.']
+n2_model_fashion_popout_z_study_1 <- n2_model_fashion_popout_study_1$coefficients[2, 'Robust z']
+n2_model_fashion_popout_p_study_1 <- (1 - pnorm(abs(n2_model_fashion_popout_z_study_1))) * 2
+
+p3_model_fashion_popout_study_1 <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "p3" & category == "fashion"& is_word == TRUE & electrode == "Cz",
+    data = time_window_data_study_1,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p3_model_fashion_popout_beta_study_1 <- p3_model_fashion_popout_study_1$coefficients[2, 'Estimate']
+p3_model_fashion_popout_se_study_1 <- p3_model_fashion_popout_study_1$coefficients[2, 'Robust S.E.']
+p3_model_fashion_popout_z_study_1 <- p3_model_fashion_popout_study_1$coefficients[2, 'Robust z']
+p3_model_fashion_popout_p_study_1 <- (1 - pnorm(abs(p3_model_fashion_popout_z_study_1))) * 2
+
+lpp_model_fashion_popout_study_1 <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "lpp" & category == "fashion"& is_word == TRUE & electrode == "Cz",
+    data = time_window_data_study_1,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+lpp_model_fashion_popout_beta_study_1 <- lpp_model_fashion_popout_study_1$coefficients[2, 'Estimate']
+lpp_model_fashion_popout_se_study_1 <- lpp_model_fashion_popout_study_1$coefficients[2, 'Robust S.E.']
+lpp_model_fashion_popout_z_study_1 <- lpp_model_fashion_popout_study_1$coefficients[2, 'Robust z']
+lpp_model_fashion_popout_p_study_1 <- (1 - pnorm(abs(lpp_model_fashion_popout_z_study_1))) * 2
+
+```
+
+In the fashion condition, there fashion words elicited a more positive ERP than non-fashion words in the P3 window ($\beta$ = `r p3_model_fashion_popout_beta_study_1 %>% round(3)`, *SE* = `r p3_model_fashion_popout_se_study_1 %>% round(3)`, *z* = `r p3_model_fashion_popout_z_study_1 %>% round(3)`, *p* = `r p3_model_fashion_popout_p_study_1 %>% format(scientific=FALSE)`).
+There was no significant difference in the P2 window, ($\beta$ = `r p2_model_fashion_popout_beta_study_1 %>% round(3)`, *SE* = `r p2_model_fashion_popout_se_study_1 %>% round(3)`, *z* = `r p2_model_fashion_popout_z_study_1 %>% round(3)`, *p* = `r p2_model_fashion_popout_p_study_1 %>% format(scientific=FALSE)`), N2 window ($\beta$ = `r n2_model_fashion_popout_beta_study_1 %>% round(3)`, *SE* = `r n2_model_fashion_popout_se_study_1 %>% round(3)`, *z* = `r n2_model_fashion_popout_z_study_1 %>% round(3)`, *p* = `r n2_model_fashion_popout_p_study_1 %>% format(scientific=FALSE)`), and LPP window ($\beta$ = `r lpp_model_fashion_popout_beta_study_1 %>% round(3)`, *SE* = `r lpp_model_fashion_popout_se_study_1 %>% round(3)`, *z* = `r lpp_model_fashion_popout_z_study_1 %>% round(3)`, *p* = `r lpp_model_fashion_popout_p_study_1 %>% format(scientific=FALSE)`).
+
+## Experiment 2
+
+### Methods
 
@@
 #| include: false
-osf_retrieve_node("ngtha") %>%
+osf_retrieve_node("x5byq") %>%
   osf_ls_files() %>%
-  osf_download(path="data/final", conflicts="skip")
+  osf_download(path="data/phase_2/final", conflicts="skip")
 ```
@@
 
-## Participants
+#### Participants
 
@@
 
-exclude_for_eeg_quality <- c("34")
-```
-
-```{r}
-#| label: Flip responses for subject 01, 36 moral words
-#| include: false
-
-behavioral_data <- behavioral_data %>%
-  mutate(correct = ifelse(subject_id == "01", !correct, correct)) %>%
-  mutate(correct = ifelse(subject_id == "36" & phase == "moral", !correct, correct))
+exclude_for_eeg_quality <- c()
 ```
@@
 
-# Results
+### Results
 
-## Behavioral
+#### Behavioral
 
@@
 
-We found a pop-out effect fashion words, but not moral words.
-
-In the moral condition, participants were `r mean_moral_in_category`% accurate for moral words and `r mean_moral_out_category`% accurate for non-moral words.
-This difference was not statistically significant in the GEE model, $\beta$ = `r coefficient_moral_pop_out %>% round(3)`, *SE* = `r coefficient_moral_pop_out_se %>% round(3)`, *z* = `r z_moral_pop_out %>% round(3)`, *p* = `r p_moral_pop_out %>% format(scientific=FALSE)`.
-
-In the fashion condition, participants were `r mean_fashion_in_category`% accurate for fashion words and `r mean_fashion_out_category`% accurate for non-fashion words.
-This difference was statistically significant in the GEE model, $\beta$ = `r coefficient_fashion_pop_out`, *SE* = `r coefficient_fashion_pop_out_se %>% round(3)`, *z* = `r z_fashion_pop_out %>% round(3)`, *p* = `r p_fashion_pop_out %>% format(scientific=FALSE)`.
-
-## EEG
+#### EEG
 
@@
   filter(!subject %in% excluded_subjects)
-```
-
-```{r}
-#| label: Flip subject 01s, 1/2 36s responses
-#| include: false
-
-eeg_data <- eeg_data %>%
-  mutate(correct = ifelse(subject == "01", !correct, correct)) %>%
-  mutate(correct = ifelse(subject == "36" & word_type == "moral", !correct, correct))
 ```
@@
 ```{r}
-#| label: Define time windows
-#| include: false
-p2.window.start <- 200
-p2.window.end <- 250
-n2.window.start <- 250
-n2.window.end <- 350
-p3.window.start <- 350
-p3.window.end <- 600
-lpp.window.start <- 600
-lpp.window.end <- 800
-
-# vectorized function for indicating time window
-get_time_window <- function(t){
-  ifelse(t >= p2.window.start & t < p2.window.end, "p2",
-  ifelse(t >= n2.window.start & t < n2.window.end, "n2",
-  ifelse(t >= p3.window.start & t < p3.window.end, "p3",
-  ifelse(t >= lpp.window.start & t < lpp.window.end, "lpp",
-  "other"))))
-}
-```
-
-```{r}
 #| label: Calculate mean voltage in all time windows for each trial
@@
 ```
-
-### Words vs. Non-Words
-
-Following Gantman and Van Bavel, we looked for word vs. non-word ERP effects at each time window at electrode Pz.
-
-```{r}
-#| label: Run GEE models for all time windows, moral data word non-word
-#| include: false
-
-p2_model_moral_word_nonword <- gee(v ~ is_word,
-    id = subject,
-    subset = erp_component == "p2" & category == "moral" & electrode == "Pz",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-p2_model_moral_word_nonword_beta <- p2_model_moral_word_nonword$coefficients[2, 'Estimate']
-p2_model_moral_word_nonword_se <- p2_model_moral_word_nonword$coefficients[2, 'Robust S.E.']
-p2_model_moral_word_nonword_z <- p2_model_moral_word_nonword$coefficients[2, 'Robust z']
-p2_model_moral_word_nonword_p <- (1 - pnorm(abs(p2_model_moral_word_nonword_z))) * 2
-
-n2_model_moral_word_nonword <- gee(v ~ is_word,
-    id = subject,
-    subset = erp_component == "n2" & category == "moral" & electrode == "Pz",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-n2_model_moral_word_nonword_beta <- n2_model_moral_word_nonword$coefficients[2, 'Estimate']
-n2_model_moral_word_nonword_se <- n2_model_moral_word_nonword$coefficients[2, 'Robust S.E.']
-n2_model_moral_word_nonword_z <- n2_model_moral_word_nonword$coefficients[2, 'Robust z']
-n2_model_moral_word_nonword_p <- (1 - pnorm(abs(n2_model_moral_word_nonword_z))) * 2
-
-p3_model_moral_word_nonword <- gee(v ~ is_word,
-    id = subject,
-    subset = erp_component == "p3" & category == "moral" & electrode == "Pz",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-p3_model_moral_word_nonword_beta <- p3_model_moral_word_nonword$coefficients[2, 'Estimate']
-p3_model_moral_word_nonword_se <- p3_model_moral_word_nonword$coefficients[2, 'Robust S.E.']
-p3_model_moral_word_nonword_z <- p3_model_moral_word_nonword$coefficients[2, 'Robust z']
-p3_model_moral_word_nonword_p <- (1 - pnorm(abs(p3_model_moral_word_nonword_z))) * 2
-
-lpp_model_moral_word_nonword <- gee(v ~ is_word,
-    id = subject,
-    subset = erp_component == "lpp" & category == "moral" & electrode == "Pz",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-lpp_model_moral_word_nonword_beta <- lpp_model_moral_word_nonword$coefficients[2, 'Estimate']
-lpp_model_moral_word_nonword_se <- lpp_model_moral_word_nonword$coefficients[2, 'Robust S.E.']
-lpp_model_moral_word_nonword_z <- lpp_model_moral_word_nonword$coefficients[2, 'Robust z']
-lpp_model_moral_word_nonword_p <- (1 - pnorm(abs(lpp_model_moral_word_nonword_z))) * 2
-```
-
-In the moral condition, words elicited a more positive ERP in the P2 window ($\beta$ = `r p2_model_moral_word_nonword_beta %>% round(3)`, *SE* = `r p2_model_moral_word_nonword_se %>% round(3)`, *z* = `r p2_model_moral_word_nonword_z %>% round(3)`, *p* = `r p2_model_moral_word_nonword_p %>% format(scientific=FALSE)`), N2 window ($\beta$ = `r n2_model_moral_word_nonword_beta %>% round(3)`, *SE* = `r n2_model_moral_word_nonword_se %>% round(3)`, *z* = `r n2_model_moral_word_nonword_z %>% round(3)`, *p* = `r n2_model_moral_word_nonword_p %>% format(scientific=FALSE)`), and P3 window ($\beta$ = `r p3_model_moral_word_nonword_beta %>% round(3)`, *SE* = `r p3_model_moral_word_nonword_se %>% round(3)`, *z* = `r p3_model_moral_word_nonword_z %>% round(3)`, *p* = `r p3_model_moral_word_nonword_p %>% format(scientific=FALSE)`).
-There was no significant effect in the LPP window ($\beta$ = `r lpp_model_moral_word_nonword_beta %>% round(3)`, *SE* = `r lpp_model_moral_word_nonword_se %>% round(3)`, *z* = `r lpp_model_moral_word_nonword_z %>% round(3)`, *p* = `r lpp_model_moral_word_nonword_p %>% format(scientific=FALSE)`).
-
-```{r}
-#| label: Run GEE models for all time windows, fashion data word non-word
-#| include: false
-
-p2_model_fashion_word_nonword <- gee(v ~ is_word,
-    id = subject,
-    subset = erp_component == "p2" & category == "fashion" & electrode == "Pz",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-p2_model_fashion_word_nonword_beta <- p2_model_fashion_word_nonword$coefficients[2, 'Estimate']
-p2_model_fashion_word_nonword_se <- p2_model_fashion_word_nonword$coefficients[2, 'Robust S.E.']
-p2_model_fashion_word_nonword_z <- p2_model_fashion_word_nonword$coefficients[2, 'Robust z']
-p2_model_fashion_word_nonword_p <- (1 - pnorm(abs(p2_model_fashion_word_nonword_z))) * 2
-
-n2_model_fashion_word_nonword <- gee(v ~ is_word,
-    id = subject,
-    subset = erp_component == "n2" & category == "fashion" & electrode == "Pz",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-n2_model_fashion_word_nonword_beta <- n2_model_fashion_word_nonword$coefficients[2, 'Estimate']
-n2_model_fashion_word_nonword_se <- n2_model_fashion_word_nonword$coefficients[2, 'Robust S.E.']
-n2_model_fashion_word_nonword_z <- n2_model_fashion_word_nonword$coefficients[2, 'Robust z']
-n2_model_fashion_word_nonword_p <- (1 - pnorm(abs(n2_model_fashion_word_nonword_z))) * 2
-
-p3_model_fashion_word_nonword <- gee(v ~ is_word,
-    id = subject,
-    subset = erp_component == "p3" & category == "fashion" & electrode == "Pz",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-p3_model_fashion_word_nonword_beta <- p3_model_fashion_word_nonword$coefficients[2, 'Estimate']
-p3_model_fashion_word_nonword_se <- p3_model_fashion_word_nonword$coefficients[2, 'Robust S.E.']
-p3_model_fashion_word_nonword_z <- p3_model_fashion_word_nonword$coefficients[2, 'Robust z']
-p3_model_fashion_word_nonword_p <- (1 - pnorm(abs(p3_model_fashion_word_nonword_z))) * 2
-
-lpp_model_fashion_word_nonword <- gee(v ~ is_word,
-    id = subject,
-    subset = erp_component == "lpp" & category == "fashion" & electrode == "Pz",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-lpp_model_fashion_word_nonword_beta <- lpp_model_fashion_word_nonword$coefficients[2, 'Estimate']
-lpp_model_fashion_word_nonword_se <- lpp_model_fashion_word_nonword$coefficients[2, 'Robust S.E.']
-lpp_model_fashion_word_nonword_z <- lpp_model_fashion_word_nonword$coefficients[2, 'Robust z']
-lpp_model_fashion_word_nonword_p <- (1 - pnorm(abs(lpp_model_fashion_word_nonword_z))) * 2
-
-```
-
-In the fashion condition, words elicited a more positive ERP only in the P2 window ($\beta$ = `r p2_model_fashion_word_nonword_beta %>% round(3)`, *SE* = `r p2_model_fashion_word_nonword_se %>% round(3)`, *z* = `r p2_model_fashion_word_nonword_z %>% round(3)`, *p* = `r p2_model_fashion_word_nonword_p %>% format(scientific=FALSE)`).
-There was no significant difference in the N2 window ($\beta$ = `r n2_model_fashion_word_nonword_beta %>% round(3)`, *SE* = `r n2_model_fashion_word_nonword_se %>% round(3)`, *z* = `r n2_model_fashion_word_nonword_z %>% round(3)`, *p* = `r n2_model_fashion_word_nonword_p %>% format(scientific=FALSE)`), P3 window ($\beta$ = `r p3_model_fashion_word_nonword_beta %>% round(3)`, *SE* = `r p3_model_fashion_word_nonword_se %>% round(3)`, *z* = `r p3_model_fashion_word_nonword_z %>% round(3)`, *p* = `r p3_model_fashion_word_nonword_p %>% format(scientific=FALSE)`), and LPP window ($\beta$ = `r lpp_model_fashion_word_nonword_beta %>% round(3)`, *SE* = `r lpp_model_fashion_word_nonword_se %>% round(3)`, *z* = `r lpp_model_fashion_word_nonword_z %>% round(3)`, *p* = `r lpp_model_fashion_word_nonword_p %>% format(scientific=FALSE)`).
-
-### Pop-out effects
-
-Also following Gantman and Van Bavel, we looked for ERP differences related to the category vs. non-category distinction in all four time windows at electrode Cz.
-
-```{r}
-#| label: Run GEE models for all time windows, moral data pop-out
-#| include: false
-
-p2_model_moral_popout <- gee(v ~ word_category,
-    id = subject,
-    subset = erp_component == "p2" & category == "moral" & is_word == TRUE & electrode == "Cz",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-p2_model_moral_popout_beta <- p2_model_moral_popout$coefficients[2, 'Estimate']
-p2_model_moral_popout_se <- p2_model_moral_popout$coefficients[2, 'Robust S.E.']
-p2_model_moral_popout_z <- p2_model_moral_popout$coefficients[2, 'Robust z']
-p2_model_moral_popout_p <- (1 - pnorm(abs(p2_model_moral_popout_z))) * 2
-
-n2_model_moral_popout <- gee(v ~ word_category,
-    id = subject,
-    subset = erp_component == "n2" & category == "moral" & is_word == TRUE & electrode == "Cz",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-n2_model_moral_popout_beta <- n2_model_moral_popout$coefficients[2, 'Estimate']
-n2_model_moral_popout_se <- n2_model_moral_popout$coefficients[2, 'Robust S.E.']
-n2_model_moral_popout_z <- n2_model_moral_popout$coefficients[2, 'Robust z']
-n2_model_moral_popout_p <- (1 - pnorm(abs(n2_model_moral_popout_z))) * 2
-
-p3_model_moral_popout <- gee(v ~ word_category,
-    id = subject,
-    subset = erp_component == "p3" & category == "moral"& is_word == TRUE & electrode == "Cz",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-p3_model_moral_popout_beta <- p3_model_moral_popout$coefficients[2, 'Estimate']
-p3_model_moral_popout_se <- p3_model_moral_popout$coefficients[2, 'Robust S.E.']
-p3_model_moral_popout_z <- p3_model_moral_popout$coefficients[2, 'Robust z']
-p3_model_moral_popout_p <- (1 - pnorm(abs(p3_model_moral_popout_z))) * 2
-
-lpp_model_moral_popout <- gee(v ~ word_category,
-    id = subject,
-    subset = erp_component == "lpp" & category == "moral"& is_word == TRUE & electrode == "Cz",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-lpp_model_moral_popout_beta <- lpp_model_moral_popout$coefficients[2, 'Estimate']
-lpp_model_moral_popout_se <- lpp_model_moral_popout$coefficients[2, 'Robust S.E.']
-lpp_model_moral_popout_z <- lpp_model_moral_popout$coefficients[2, 'Robust z']
-lpp_model_moral_popout_p <- (1 - pnorm(abs(lpp_model_moral_popout_z))) * 2
-
-```
-
-In the moral condition, there was a significant difference between moral and non-moral words in the P2 window ($\beta$ = `r p2_model_moral_popout_beta %>% round(3)`, *SE* = `r p2_model_moral_popout_se %>% round(3)`, *z* = `r p2_model_moral_popout_z %>% round(3)`, *p* = `r p2_model_moral_popout_p %>% format(scientific=FALSE)`) and the LPP window ($\beta$ = `r lpp_model_moral_popout_beta %>% round(3)`, *SE* = `r lpp_model_moral_popout_se %>% round(3)`, *z* = `r lpp_model_moral_popout_z %>% round(3)`, *p* = `r lpp_model_moral_popout_p %>% format(scientific=FALSE)`).
-However, in both of these cases the effect was in the *opposite* direction as the original, with non-moral words having a more positive ERP.
-There was no significant difference between moral and non-moral words in the N2 window ($\beta$ = `r n2_model_moral_popout_beta %>% round(3)`, *SE* = `r n2_model_moral_popout_se %>% round(3)`, *z* = `r n2_model_moral_popout_z %>% round(3)`, *p* = `r n2_model_moral_popout_p %>% format(scientific=FALSE)`) and P3 window ($\beta$ = `r p3_model_moral_popout_beta %>% round(3)`, *SE* = `r p3_model_moral_popout_se %>% round(3)`, *z* = `r p3_model_moral_popout_z %>% round(3)`, *p* = `r p3_model_moral_popout_p %>% format(scientific=FALSE)`).
-
-```{r}
-#| label: Run GEE models for all time windows, fashion data pop-out
-#| include: false
-
-p2_model_fashion_popout <- gee(v ~ word_category,
-    id = subject,
-    subset = erp_component == "p2" & category == "fashion" & is_word == TRUE & electrode == "Cz",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-p2_model_fashion_popout_beta <- p2_model_fashion_popout$coefficients[2, 'Estimate']
-p2_model_fashion_popout_se <- p2_model_fashion_popout$coefficients[2, 'Robust S.E.']
-p2_model_fashion_popout_z <- p2_model_fashion_popout$coefficients[2, 'Robust z']
-p2_model_fashion_popout_p <- (1 - pnorm(abs(p2_model_fashion_popout_z))) * 2
-
-n2_model_fashion_popout <- gee(v ~ word_category,
-    id = subject,
-    subset = erp_component == "n2" & category == "fashion"& is_word == TRUE & electrode == "Cz",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-n2_model_fashion_popout_beta <- n2_model_fashion_popout$coefficients[2, 'Estimate']
-n2_model_fashion_popout_se <- n2_model_fashion_popout$coefficients[2, 'Robust S.E.']
-n2_model_fashion_popout_z <- n2_model_fashion_popout$coefficients[2, 'Robust z']
-n2_model_fashion_popout_p <- (1 - pnorm(abs(n2_model_fashion_popout_z))) * 2
-
-p3_model_fashion_popout <- gee(v ~ word_category,
-    id = subject,
-    subset = erp_component == "p3" & category == "fashion"& is_word == TRUE & electrode == "Cz",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-p3_model_fashion_popout_beta <- p3_model_fashion_popout$coefficients[2, 'Estimate']
-p3_model_fashion_popout_se <- p3_model_fashion_popout$coefficients[2, 'Robust S.E.']
-p3_model_fashion_popout_z <- p3_model_fashion_popout$coefficients[2, 'Robust z']
-p3_model_fashion_popout_p <- (1 - pnorm(abs(p3_model_fashion_popout_z))) * 2
-
-lpp_model_fashion_popout <- gee(v ~ word_category,
-    id = subject,
-    subset = erp_component == "lpp" & category == "fashion"& is_word == TRUE & electrode == "Cz",
-    data = time_window_data,
-    family = gaussian,
-    corstr = "exchangeable") %>% summary()
-
-lpp_model_fashion_popout_beta <- lpp_model_fashion_popout$coefficients[2, 'Estimate']
-lpp_model_fashion_popout_se <- lpp_model_fashion_popout$coefficients[2, 'Robust S.E.']
-lpp_model_fashion_popout_z <- lpp_model_fashion_popout$coefficients[2, 'Robust z']
-lpp_model_fashion_popout_p <- (1 - pnorm(abs(lpp_model_fashion_popout_z))) * 2
-
-```
-
-In the fashion condition, there fashion words elicited a more positive ERP than non-fashion words in the P3 window ($\beta$ = `r p3_model_fashion_popout_beta %>% round(3)`, *SE* = `r p3_model_fashion_popout_se %>% round(3)`, *z* = `r p3_model_fashion_popout_z %>% round(3)`, *p* = `r p3_model_fashion_popout_p %>% format(scientific=FALSE)`).
-There was no significant difference in the P2 window, ($\beta$ = `r p2_model_fashion_popout_beta %>% round(3)`, *SE* = `r p2_model_fashion_popout_se %>% round(3)`, *z* = `r p2_model_fashion_popout_z %>% round(3)`, *p* = `r p2_model_fashion_popout_p %>% format(scientific=FALSE)`), N2 window ($\beta$ = `r n2_model_fashion_popout_beta %>% round(3)`, *SE* = `r n2_model_fashion_popout_se %>% round(3)`, *z* = `r n2_model_fashion_popout_z %>% round(3)`, *p* = `r n2_model_fashion_popout_p %>% format(scientific=FALSE)`), and LPP window ($\beta$ = `r lpp_model_fashion_popout_beta %>% round(3)`, *SE* = `r lpp_model_fashion_popout_se %>% round(3)`, *z* = `r lpp_model_fashion_popout_z %>% round(3)`, *p* = `r lpp_model_fashion_popout_p %>% format(scientific=FALSE)`).

### 2024-03-21 preprocessing/merge-behavioral-local.R

@@ -3,9 +3,7 @@ library(dplyr)
 library(readr)
 library(tidyr)
 
-
 which_phase <- "phase_2"
-
 
 behavior.files <- list.files(paste0('data/', which_phase, '/raw/beh'), pattern="json", full.names = T)
 

### 2024-03-29 manuscript.qmd
add trailing / for osx compatibility?

@@
   osf_ls_files() %>%
-  osf_download(path="data/phase_1/final", conflicts="skip")
+  osf_download(path="data/phase_1/final/", conflicts="skip")
 ```
@@
   osf_ls_files() %>%
-  osf_download(path="data/phase_2/final", conflicts="skip")
+  osf_download(path="data/phase_2/final/", conflicts="skip")
 ```

### 2024-04-01 manuscript.qmd
fix error in GEE model

--- 2024-03-21 manuscript.qmd
@@
   mutate(correct = ifelse(subject == "01", !correct, correct)) %>%
-  mutate(correct = ifelse(subject == "36" & word_type == "moral", !correct, correct))
+  mutate(correct = ifelse(subject == "36" & (word_type == "moral" | word_type == "non-moral"), !correct, correct))
 ```
@@
 
-time_window_data_study_1 <- eeg_data_study_1 %>%
+time_window_data_study_1 <- eeg_data_key_corrected_study_1 %>%
   filter(electrode %in% c("Cz", "Pz")) %>%
@@
   filter(erp_component != "other") %>%
-  group_by(subject, electrode, word_type, is_word, erp_component) %>%
+  group_by(subject, event_id, electrode, word_type, is_word, erp_component) %>%
   summarize(v = mean(v)) %>%
@@
 
-In the moral condition, there were no significant differences between moral and non-moral words in the P2 window ($\beta$ = `r p2_model_moral_popout_beta_study_1 %>% round(3)`, *SE* = `r p2_model_moral_popout_se_study_1 %>% round(3)`, *z* = `r p2_model_moral_popout_z_study_1 %>% round(3)`, *p* = `r p2_model_moral_popout_p_study_1 %>% format(scientific=FALSE)`), N2 window ($\beta$ = `r n2_model_moral_popout_beta_study_1 %>% round(3)`, *SE* = `r n2_model_moral_popout_se_study_1 %>% round(3)`, *z* = `r n2_model_moral_popout_z_study_1 %>% round(3)`, *p* = `r n2_model_moral_popout_p_study_1 %>% format(scientific=FALSE)`), P3 window ($\beta$ = `r p3_model_moral_popout_beta_study_1 %>% round(3)`, *SE* = `r p3_model_moral_popout_se_study_1 %>% round(3)`, *z* = `r p3_model_moral_popout_z_study_1 %>% round(3)`, *p* = `r p3_model_moral_popout_p_study_1 %>% format(scientific=FALSE)`), and the LPP window ($\beta$ = `r lpp_model_moral_popout_beta_study_1 %>% round(3)`, *SE* = `r lpp_model_moral_popout_se_study_1 %>% round(3)`, *z* = `r lpp_model_moral_popout_z_study_1 %>% round(3)`, *p* = `r lpp_model_moral_popout_p_study_1 %>% format(scientific=FALSE)`).
+In the moral condition, there was a significant difference between moral and non-moral words in the P2 window ($\beta$ = `r p2_model_moral_popout_beta_study_1 %>% round(3)`, *SE* = `r p2_model_moral_popout_se_study_1 %>% round(3)`, *z* = `r p2_model_moral_popout_z_study_1 %>% round(3)`, *p* = `r p2_model_moral_popout_p_study_1 %>% format(scientific=FALSE)`), but this difference was in the opposite direction predicted by Gantman et al.
+(2020).
+There were no significant differences between moral and non-moral words in the N2 window ($\beta$ = `r n2_model_moral_popout_beta_study_1 %>% round(3)`, *SE* = `r n2_model_moral_popout_se_study_1 %>% round(3)`, *z* = `r n2_model_moral_popout_z_study_1 %>% round(3)`, *p* = `r n2_model_moral_popout_p_study_1 %>% format(scientific=FALSE)`), P3 window ($\beta$ = `r p3_model_moral_popout_beta_study_1 %>% round(3)`, *SE* = `r p3_model_moral_popout_se_study_1 %>% round(3)`, *z* = `r p3_model_moral_popout_z_study_1 %>% round(3)`, *p* = `r p3_model_moral_popout_p_study_1 %>% format(scientific=FALSE)`), and the LPP window ($\beta$ = `r lpp_model_moral_popout_beta_study_1 %>% round(3)`, *SE* = `r lpp_model_moral_popout_se_study_1 %>% round(3)`, *z* = `r lpp_model_moral_popout_z_study_1 %>% round(3)`, *p* = `r lpp_model_moral_popout_p_study_1 %>% format(scientific=FALSE)`).
 
@@
 
-In the fashion condition, there fashion words elicited a more positive ERP than non-fashion words in the P3 window ($\beta$ = `r p3_model_fashion_popout_beta_study_1 %>% round(3)`, *SE* = `r p3_model_fashion_popout_se_study_1 %>% round(3)`, *z* = `r p3_model_fashion_popout_z_study_1 %>% round(3)`, *p* = `r p3_model_fashion_popout_p_study_1 %>% format(scientific=FALSE)`).
-There was no significant difference in the P2 window, ($\beta$ = `r p2_model_fashion_popout_beta_study_1 %>% round(3)`, *SE* = `r p2_model_fashion_popout_se_study_1 %>% round(3)`, *z* = `r p2_model_fashion_popout_z_study_1 %>% round(3)`, *p* = `r p2_model_fashion_popout_p_study_1 %>% format(scientific=FALSE)`), N2 window ($\beta$ = `r n2_model_fashion_popout_beta_study_1 %>% round(3)`, *SE* = `r n2_model_fashion_popout_se_study_1 %>% round(3)`, *z* = `r n2_model_fashion_popout_z_study_1 %>% round(3)`, *p* = `r n2_model_fashion_popout_p_study_1 %>% format(scientific=FALSE)`), and LPP window ($\beta$ = `r lpp_model_fashion_popout_beta_study_1 %>% round(3)`, *SE* = `r lpp_model_fashion_popout_se_study_1 %>% round(3)`, *z* = `r lpp_model_fashion_popout_z_study_1 %>% round(3)`, *p* = `r lpp_model_fashion_popout_p_study_1 %>% format(scientific=FALSE)`).
+In the fashion condition, there fashion words elicited a more positive ERP than non-fashion words in the P3 window ($\beta$ = `r p3_model_fashion_popout_beta_study_1 %>% round(3)`, *SE* = `r p3_model_fashion_popout_se_study_1 %>% round(3)`, *z* = `r p3_model_fashion_popout_z_study_1 %>% round(3)`, *p* = `r p3_model_fashion_popout_p_study_1 %>% format(scientific=FALSE)`) and LPP window ($\beta$ = `r lpp_model_fashion_popout_beta_study_1 %>% round(3)`, *SE* = `r lpp_model_fashion_popout_se_study_1 %>% round(3)`, *z* = `r lpp_model_fashion_popout_z_study_1 %>% round(3)`, *p* = `r lpp_model_fashion_popout_p_study_1 %>% format(scientific=FALSE)`).
+There was no significant difference in the P2 window ($\beta$ = `r p2_model_fashion_popout_beta_study_1 %>% round(3)`, *SE* = `r p2_model_fashion_popout_se_study_1 %>% round(3)`, *z* = `r p2_model_fashion_popout_z_study_1 %>% round(3)`, *p* = `r p2_model_fashion_popout_p_study_1 %>% format(scientific=FALSE)`) and N2 window ($\beta$ = `r n2_model_fashion_popout_beta_study_1 %>% round(3)`, *SE* = `r n2_model_fashion_popout_se_study_1 %>% round(3)`, *z* = `r n2_model_fashion_popout_z_study_1 %>% round(3)`, *p* = `r n2_model_fashion_popout_p_study_1 %>% format(scientific=FALSE)`).
 

### 2024-04-01 tmp for testing.R

@@ -1,6 +1,6 @@
 source("preprocessing/preprocessing-eeg-functions.R")
 
-subject <- "01"
+subject <- "24"
 
 eeg.file <- list.files('data/raw/eeg', pattern=paste0("subject-", subject), full.names = T)
 beh.file <- paste0('data/raw/beh/219_2024_behavioral_', subject,'.json')
@@ -8,8 +8,8 @@ beh.file <- paste0('data/raw/beh/219_2024_behavioral_', subject,'.json')
 sampling_rate = 500
 filter_low = 0.1
 filter_high = 30
-segment_begin = -200
-segment_end = 1000
+segment_begin = -400
+segment_end = 1200
 segment_offset = 0
 bad_segment_range = 500
 eye_threshold = 70
@@ -17,10 +17,148 @@ which_electrodes = c("Fp1", "Fp2", "Cz", "Pz")
 eye_channels=c("Fp1", "Fp2")
 target_channels=c("Cz", "Pz")
 
-epochs <- read_eeg_tidy(eeg.file, beh.file, which_electrodes) %>%
-  #linked_ears_rereference() %>%
-  bandpass(low=filter_low, high=filter_high, sampling_rate=sampling_rate) %>%
-  #notch(low=notch_filter_low, high=notch_filter_high, sampling_rate=sampling_rate) %>%
+# epochs <- read_eeg_tidy(eeg.file, beh.file, which_electrodes) %>%
+#   #linked_ears_rereference() %>%
+#   bandpass(low=filter_low, high=filter_high, sampling_rate=sampling_rate) %>%
+#   #notch(low=notch_filter_low, high=notch_filter_high, sampling_rate=sampling_rate) %>%
+#   segment(start = segment_begin, end = segment_end, offset=segment_offset, sampling_rate=sampling_rate) %>%
+#   baseline_correct()
+
+
+data <- read_eeg_tidy(eeg.file, beh.file, which_electrodes)
+
+sample_window <- 100000:105000
+
+unfiltered_data_cz <- data$signals %>%
+  dplyr::filter(electrode == "Cz") %>%
+  dplyr::filter(sample_id %in% sample_window)
+
+library(ggplot2)
+ggplot(unfiltered_data_cz, aes(x=sample_id, y=v)) +
+  geom_line() +
+  labs(title="Unfiltered Cz data", x="Sample ID", y="Voltage (uV)")+
+  theme_minimal()
+
[…]

### 2024-04-03 preprocessing/preprocessing-eeg-functions.R
fix parameter name (did not affect data processing because of luckily-named global variable!)

@@ -5,7 +5,7 @@ library(ravetools)
 library(eegkit)
 source('preprocessing/extract-events.R')
 
-preprocess_eeg <- function(file, beh.file, subject_id, sampling_rate=500, filter_low=0.1, filter_high=70, notch_filter_low=59, notch_filter_high=61, segment_begin=-100, segment_end=1000, segment_offset=0, bad_segment_range=200, eye_threshold=70, which_electrodes=c('Cz', 'Fz', 'Fp1', 'Fp2')){
+preprocess_eeg <- function(eeg.file, beh.file, subject_id, sampling_rate=500, filter_low=0.1, filter_high=70, notch_filter_low=59, notch_filter_high=61, segment_begin=-100, segment_end=1000, segment_offset=0, bad_segment_range=200, eye_threshold=70, which_electrodes=c('Cz', 'Fz', 'Fp1', 'Fp2')){
   data <- read_eeg_tidy(eeg.file, beh.file, which_electrodes) %>%
     #linked_ears_rereference() %>%
     bandpass(low=filter_low, high=filter_high, sampling_rate=sampling_rate) %>%

### 2024-04-03 preprocessing/run_preprocessing_local_machine.R

@@ -21,7 +21,7 @@ for(subject in subjects){
     beh.file <- paste0('data/', which_phase, '/raw/beh/219_2024_', if_else(which_phase=="phase_2", "v2_", ""), 'behavioral_', subject,'.json')
     
     preprocessed.data <- preprocess_eeg(
-      file = eeg.file, 
+      eeg.file = eeg.file, 
       beh.file = beh.file,
       subject_id = subject,
       sampling_rate = 500,

### 2024-04-10 manuscript.qmd
automate the eeg quality exclusion

@@
 
+```{r}
+#| label: Load study 1 eeg data
+#| include: false
+
+eeg_data_study_1 <- read_csv("data/phase_1/final/eeg.csv", col_types = "cdcllcdc")
+```
+
+```{r}
+#| label: Flip study 1 subject 01s, 1/2 36s responses
+#| include: false
+
+eeg_data_key_corrected_study_1 <- eeg_data_study_1 %>%
+  mutate(correct = ifelse(subject == "01", !correct, correct)) %>%
+  mutate(correct = ifelse(subject == "36" & (word_type == "moral" | word_type == "non-moral"), !correct, correct))
+```
+
+```{r}
+#| label: Count the number of study 1 good segments per subject
+#| include: false
+
+count_good_trials_study_1 <- eeg_data_study_1 %>%
+  filter(t==0, electrode=="Cz") %>%
+  group_by(subject) %>%
+  summarize(n=n()) %>%
+  mutate(percent = (n/600)*100)
+
+mean_good_trials_study_1 <- mean(count_good_trials_study_1$n)
+sd_good_trials_study_1 <- sd(count_good_trials_study_1$n)
+
+```
+
 #### Participants
@@
 
-exclude_for_eeg_quality_study_1 <- c("34")
+exclude_for_eeg_quality_study_1 <- count_good_trials_study_1 %>%
+  filter(percent < 75) %>% 
+  pull(subject)
 ```
@@
 ```{r}
-#| label: Load study 1 eeg data
-#| include: false
-
-eeg_data_study_1 <- read_csv("data/phase_1/final/eeg.csv", col_types = "cdcllcdc") %>%
-  filter(!subject %in% excluded_subjects_study_1)
-```
-
-```{r}
-#| label: Flip study 1 subject 01s, 1/2 36s responses
-#| include: false
-
-eeg_data_key_corrected_study_1 <- eeg_data_study_1 %>%
-  mutate(correct = ifelse(subject == "01", !correct, correct)) %>%
-  mutate(correct = ifelse(subject == "36" & (word_type == "moral" | word_type == "non-moral"), !correct, correct))
-```
-
-```{r}
 #| label: Compute study 1 subject ERPs
@@
   theme(panel.grid = element_blank())
-```
-
-```{r}
-#| label: Count the number of study 1 good segments per subject
-#| include: false
-
-count_good_trials_study_1 <- eeg_data_study_1 %>%
-  filter(t==0, electrode=="Cz") %>%
-  group_by(subject) %>%
-  summarize(n=n()) %>%
-  mutate(percent = (n/600)*100)
-
-mean_good_trials_study_1 <- mean(count_good_trials_study_1$n)
-sd_good_trials_study_1 <- sd(count_good_trials_study_1$n)
-
 ```
@@
 
+```{r}
+#| label: Load eeg data
+#| include: false
+
+eeg_data <- read_csv("data/phase_2/final/eeg.csv", col_types = "cdcllcdc") %>%
+  filter(!subject %in% excluded_subjects)
+```
+
+```{r}
+#| label: Count the number of good segments per subject
+#| include: false
+
+count_good_trials <- eeg_data %>%
+  filter(t==0, electrode=="Cz") %>%
+  group_by(subject) %>%
+  summarize(n=n()) %>%
+  mutate(percent = (n/600)*100)
+
+```
+
 #### Participants
@@
 
-exclude_for_eeg_quality <- c()
+exclude_for_eeg_quality <- count_good_trials %>%
+  filter(percent < 75) %>%
+  pull(subject)
 ```
@@
 ```{r}
-#| label: Load eeg data
-#| include: false
-
-eeg_data <- read_csv("data/phase_2/final/eeg.csv", col_types = "cdcllcdc") %>%
-  filter(!subject %in% excluded_subjects)
-```
-
-```{r}
 #| label: Subject ERPs
@@
 ```{r}
-#| label: Count the number of good segments per subject
-#| include: false
-
-count_good_trials <- eeg_data %>%
-  filter(t==0, electrode=="Cz") %>%
-  group_by(subject) %>%
-  summarize(n=n()) %>%
-  mutate(percent = (n/600)*100)
-
-mean_good_trials <- mean(count_good_trials$n)
-sd_good_trials <- sd(count_good_trials$n)
-
-```
-
-```{r}
 #| label: Calculate mean voltage in all time windows for each trial

### 2024-04-10 manuscript.qmd
fix eeg data filter, add more study 2 data

@@
 subject_eeg_study_1 <- eeg_data_key_corrected_study_1 %>%
+  filter(!subject %in% excluded_subjects_study_1) %>%
   filter(electrode %in% c("Cz", "Pz")) %>%
@@
 time_window_data_study_1 <- eeg_data_key_corrected_study_1 %>%
+  filter(!subject %in% excluded_subjects_study_1) %>%
   filter(electrode %in% c("Cz", "Pz")) %>%
@@
 
-eeg_data <- read_csv("data/phase_2/final/eeg.csv", col_types = "cdcllcdc") %>%
-  filter(!subject %in% excluded_subjects)
+eeg_data <- read_csv("data/phase_2/final/eeg.csv", col_types = "cdcllcdc")
 ```
@@
 subject_eeg <- eeg_data %>%
+  filter(!subject %in% excluded_subjects) %>%
   filter(electrode %in% c("Cz", "Pz")) %>%
@@
 time_window_data <- eeg_data %>%
+  filter(!subject %in% excluded_subjects) %>%
   filter(electrode %in% c("Cz", "Pz")) %>%

### 2024-05-02 preprocessing/download-raw-data-from-osf.R
use phase 1 folder

@@ -3,11 +3,11 @@ library(dplyr)
 
 osf_retrieve_node("v7mbj") %>%
   osf_ls_files(path="Behavioral", n_max=Inf) %>%
-  osf_download(path="data/raw/beh", conflicts="skip")
+  osf_download(path="data/phase_1/raw/beh", conflicts="skip")
 
 osf_retrieve_node("v7mbj") %>%
   osf_ls_files(path="EEG", n_max=Inf) %>%
-  osf_download(path="data/raw/eeg", conflicts="skip")
+  osf_download(path="data/phase_1/raw/eeg", conflicts="skip")
 
 
 # phase 2

### 2024-05-03 preprocessing/run_preprocessing_local_machine.R
add print statement for gh action debug

@@ -8,6 +8,8 @@ subjects <- list.files(paste0('data/', which_phase, '/raw/beh/'), pattern="json"
   str_extract("[0-9]*.json") %>%
   str_remove(".json")
 
+print(subjects)
+
 for(subject in subjects){
   
   final.path <- paste0("data/", which_phase, "/preprocessed/subject-", subject,"-epochs.csv")

### 2024-05-03 preprocessing/run_preprocessing_local_machine.R
more debug for actions

@@ -4,10 +4,13 @@ source("preprocessing/preprocessing-eeg-functions.R")
 
 which_phase <- "phase_2"
 
+list.files(paste0('data/', which_phase, '/raw/beh/')
+
 subjects <- list.files(paste0('data/', which_phase, '/raw/beh/'), pattern="json") %>% 
   str_extract("[0-9]*.json") %>%
   str_remove(".json")
 
+cat(subjects)
 print(subjects)
 
 for(subject in subjects){

### 2024-05-03 preprocessing/run_preprocessing_local_machine.R
fix typo

@@ -4,7 +4,7 @@ source("preprocessing/preprocessing-eeg-functions.R")
 
 which_phase <- "phase_2"
 
-list.files(paste0('data/', which_phase, '/raw/beh/')
+list.files(paste0('data/', which_phase, '/raw/beh/'))
 
 subjects <- list.files(paste0('data/', which_phase, '/raw/beh/'), pattern="json") %>% 
   str_extract("[0-9]*.json") %>%

### 2024-05-03 preprocessing/run_preprocessing_local_machine.R
Update run_preprocessing_local_machine.R

@@ -4,13 +4,10 @@ source("preprocessing/preprocessing-eeg-functions.R")
 
 which_phase <- "phase_2"
 
-list.files(paste0('data/', which_phase, '/raw/beh/'))
-
 subjects <- list.files(paste0('data/', which_phase, '/raw/beh/'), pattern="json") %>% 
   str_extract("[0-9]*.json") %>%
   str_remove(".json")
 
-cat(subjects)
 print(subjects)
 
 for(subject in subjects){

### 2024-05-03 preprocessing/download-raw-data-from-osf.R
2 files to speed up debugging

@@ -2,20 +2,20 @@ library(osfr)
 library(dplyr)
 
 osf_retrieve_node("v7mbj") %>%
-  osf_ls_files(path="Behavioral", n_max=Inf) %>%
+  osf_ls_files(path="Behavioral", n_max=2) %>%
   osf_download(path="data/phase_1/raw/beh", conflicts="skip")
 
 osf_retrieve_node("v7mbj") %>%
-  osf_ls_files(path="EEG", n_max=Inf) %>%
+  osf_ls_files(path="EEG", n_max=2) %>%
   osf_download(path="data/phase_1/raw/eeg", conflicts="skip")
 
 
 # phase 2
 
 osf_retrieve_node("gd24h") %>%
-  osf_ls_files(path="Behavioral", n_max=Inf) %>%
+  osf_ls_files(path="Behavioral", n_max=2) %>%
   osf_download(path="data/phase_2/raw/beh", conflicts="skip")
 
 osf_retrieve_node("gd24h") %>%
-  osf_ls_files(path="EEG", n_max=Inf) %>%
+  osf_ls_files(path="EEG", n_max=2) %>%
   osf_download(path="data/phase_2/raw/eeg", conflicts="skip")

### 2024-05-03 preprocessing/run_preprocessing_local_machine.R
Update run_preprocessing_local_machine.R

@@ -8,7 +8,7 @@ subjects <- list.files(paste0('data/', which_phase, '/raw/beh/'), pattern="json"
   str_extract("[0-9]*.json") %>%
   str_remove(".json")
 
-print(subjects)
+cat(subjects)
 
 for(subject in subjects){
   

### 2024-05-03 preprocessing/preprocessing-eeg-functions.R
Update preprocessing-eeg-functions.R

@@ -1,7 +1,6 @@
 library(dplyr)
 library(tidyr)
 library(purrr)
-library(ravetools)
 library(eegkit)
 source('preprocessing/extract-events.R')
 

### 2024-05-03 preprocessing/download-raw-data-from-osf.R
go back to getting all the data

@@ -2,20 +2,20 @@ library(osfr)
 library(dplyr)
 
 osf_retrieve_node("v7mbj") %>%
-  osf_ls_files(path="Behavioral", n_max=2) %>%
+  osf_ls_files(path="Behavioral", n_max=Inf) %>%
   osf_download(path="data/phase_1/raw/beh", conflicts="skip")
 
 osf_retrieve_node("v7mbj") %>%
-  osf_ls_files(path="EEG", n_max=2) %>%
+  osf_ls_files(path="EEG", n_max=Inf) %>%
   osf_download(path="data/phase_1/raw/eeg", conflicts="skip")
 
 
 # phase 2
 
 osf_retrieve_node("gd24h") %>%
-  osf_ls_files(path="Behavioral", n_max=2) %>%
+  osf_ls_files(path="Behavioral", n_max=Inf) %>%
   osf_download(path="data/phase_2/raw/beh", conflicts="skip")
 
 osf_retrieve_node("gd24h") %>%
-  osf_ls_files(path="EEG", n_max=2) %>%
+  osf_ls_files(path="EEG", n_max=Inf) %>%
   osf_download(path="data/phase_2/raw/eeg", conflicts="skip")

### 2024-05-03 preprocessing/download-raw-data-from-osf.R
get only phase 2

@@ -1,6 +1,10 @@
 library(osfr)
 library(dplyr)
 
+get_phase_1 <- FALSE
+get_phase_2 <- TRUE
+
+if(get_phase_1){
 osf_retrieve_node("v7mbj") %>%
   osf_ls_files(path="Behavioral", n_max=Inf) %>%
   osf_download(path="data/phase_1/raw/beh", conflicts="skip")
@@ -8,10 +12,10 @@ osf_retrieve_node("v7mbj") %>%
 osf_retrieve_node("v7mbj") %>%
   osf_ls_files(path="EEG", n_max=Inf) %>%
   osf_download(path="data/phase_1/raw/eeg", conflicts="skip")
-
+}
 
 # phase 2
-
+if(get_phase_2){
 osf_retrieve_node("gd24h") %>%
   osf_ls_files(path="Behavioral", n_max=Inf) %>%
   osf_download(path="data/phase_2/raw/beh", conflicts="skip")
@@ -19,3 +23,4 @@ osf_retrieve_node("gd24h") %>%
 osf_retrieve_node("gd24h") %>%
   osf_ls_files(path="EEG", n_max=Inf) %>%
   osf_download(path="data/phase_2/raw/eeg", conflicts="skip")
+}

### 2024-05-03 preprocessing/download-raw-data-from-osf.R
revert to 2 for testing

@@ -17,10 +17,10 @@ osf_retrieve_node("v7mbj") %>%
 # phase 2
 if(get_phase_2){
 osf_retrieve_node("gd24h") %>%
-  osf_ls_files(path="Behavioral", n_max=Inf) %>%
+  osf_ls_files(path="Behavioral", n_max=2) %>%
   osf_download(path="data/phase_2/raw/beh", conflicts="skip")
 
 osf_retrieve_node("gd24h") %>%
-  osf_ls_files(path="EEG", n_max=Inf) %>%
+  osf_ls_files(path="EEG", n_max=2) %>%
   osf_download(path="data/phase_2/raw/eeg", conflicts="skip")
 }

### 2024-05-03 preprocessing/mege-local.R
add debug statement

@@ -6,6 +6,9 @@ library(dplyr)
 which_phase <- "phase_2"
 
 files <- list.files(paste0("data/", which_phase, "/preprocessed"), pattern = "*.csv", full.names = TRUE)
+
+cat(files)
+
 data <- lapply(files, function(x){
   read_csv(x, col_types = "cdcllcddlc") %>% 
     dplyr::filter(electrode %in% c("Cz", "Pz")) %>%

### 2024-05-03 preprocessing/download-raw-data-from-osf.R
Go back to all data

@@ -17,10 +17,10 @@ osf_retrieve_node("v7mbj") %>%
 # phase 2
 if(get_phase_2){
 osf_retrieve_node("gd24h") %>%
-  osf_ls_files(path="Behavioral", n_max=2) %>%
+  osf_ls_files(path="Behavioral", n_max=Inf) %>%
   osf_download(path="data/phase_2/raw/beh", conflicts="skip")
 
 osf_retrieve_node("gd24h") %>%
-  osf_ls_files(path="EEG", n_max=2) %>%
+  osf_ls_files(path="EEG", n_max=Inf) %>%
   osf_download(path="data/phase_2/raw/eeg", conflicts="skip")
 }

### 2024-05-03 manuscript.qmd
Add study 2 models

@@
 
-behavioral_data <- read_csv('data/phase_2/final/behavioral.csv')
+behavioral_data_study_2 <- read_csv('data/phase_2/final/behavioral.csv')
 ```
@@
 
-eeg_data <- read_csv("data/phase_2/final/eeg.csv", col_types = "cdcllcdc")
+eeg_data_study_2 <- read_csv("data/phase_2/final/eeg.csv", col_types = "cdcllcdc")
 ```
@@
 
-count_good_trials <- eeg_data %>%
+count_good_trials_study_2 <- eeg_data_study_2 %>%
   filter(t==0, electrode=="Cz") %>%
@@
 
-exclude_for_fashion_twice_subjects <- behavioral_data %>%
+exclude_for_fashion_twice_subjects_study_2 <- behavioral_data_study_2 %>%
   filter(phase == "fashion", task == "response") %>%
@@
 ```{r} 
+#| label: Filter out a subject who saw the first 100 trials twice because of EEG recording error
+#| include: false
+
+exclude_for_repeated_viewing_study_2 <- c("14")
+```
+
+```{r}
 #| label: Exclude very poor EEG recordings
@@
 
-exclude_for_eeg_quality <- count_good_trials %>%
+exclude_for_eeg_quality_study_2 <- count_good_trials_study_2 %>%
   filter(percent < 75) %>%
@@
 
-subject_non_response_rate <- behavioral_data %>%
+subject_non_response_rate_study_2 <- behavioral_data_study_2 %>%
   filter(phase == "moral" | phase == "fashion") %>%
@@
 
-exclude_for_non_response_subjects <- subject_non_response_rate %>%
+exclude_for_non_response_subjects_study_2 <- subject_non_response_rate_study_2 %>%
   filter(non_response_rate > 0.5) %>%
@@
 
-subject_non_word_response_rate <- behavioral_data %>%
+subject_non_word_response_rate_study_2 <- behavioral_data_study_2 %>%
   filter(phase == "moral" | phase == "fashion") %>%
@@
 
-exclude_for_non_word_response_subjects <- subject_non_word_response_rate %>%
+exclude_for_non_word_response_subjects_study_2 <- subject_non_word_response_rate_study_2 %>%
   filter(non_word_response_rate > 0.9) %>%
@@
 
-excluded_subjects <- c(exclude_for_fashion_twice_subjects, exclude_for_non_response_subjects, exclude_for_non_word_response_subjects, exclude_for_eeg_quality)
+excluded_subjects_study_2 <- c(
+  exclude_for_fashion_twice_subjects_study_2, 
+  exclude_for_non_response_subjects_study_2, 
+  exclude_for_non_word_response_subjects_study_2, 
+  exclude_for_eeg_quality_study_2,
+  exclude_for_repeated_viewing_study_2
+)
 
-behavioral_data_filtered <- behavioral_data %>%
-  filter(!subject_id %in% excluded_subjects)
+behavioral_data_filtered_study_2 <- behavioral_data_study_2 %>%
+  filter(!subject_id %in% excluded_subjects_study_2)
 ```
@@
 
-n_subjects <- behavioral_data %>% pull(subject_id) %>% unique() %>% length()
+n_subjects_study_2 <- behavioral_data_study_2 %>% pull(subject_id) %>% unique() %>% length()
 
-n_subjects_remaining <- behavioral_data_filtered %>% pull(subject_id) %>% unique() %>% length()
+n_subjects_remaining_study_2 <- behavioral_data_filtered_study_2 %>% pull(subject_id) %>% unique() %>% length()
 ```
 
-`r n_subjects` subjects participated in the study.
-After applying the exclusion criteria, `r n_subjects_remaining` subjects remain.
-`r length(exclude_for_fashion_twice_subjects)` subjects were excluded for receiving fashion words twice due to a technical error, `r length(exclude_for_eeg_quality)` subjects were excluded for having poor EEG recordings, `r length(exclude_for_non_response_subjects)` subjects were excluded for having a non-response rate greater than 50%, and `r length(exclude_for_non_word_response_subjects)` subjects were excluded for having a non-word response rate greater than 90%.
+`r n_subjects_study_2` subjects participated in the study.
+After applying the exclusion criteria, `r n_subjects_remaining_study_2` subjects remain.
+`r length(exclude_for_fashion_twice_subjects_study_2)` subject was excluded for receiving fashion words twice due to a technical error, `r length(exclude_for_repeated_viewing_study_2)` subject was excluded because they saw the first 100 trials twice due to an EEG data recording error, `r length(exclude_for_eeg_quality_study_2)` subjects were excluded for having poor EEG recordings, `r length(exclude_for_non_response_subjects_study_2)` subjects were excluded for having a non-response rate greater than 50%, and `r length(exclude_for_non_word_response_subjects_study_2)` subjects were excluded for having a non-word response rate greater than 90%.
 
@@
 
-behavioral_data_test_set <- behavioral_data_filtered %>%
+behavioral_data_test_set_study_2 <- behavioral_data_filtered_study_2 %>%
   filter(phase == "moral" | phase == "fashion") %>%
@@
 
-subject_level_accuracy <- behavioral_data_test_set %>%
+subject_level_accuracy_study_2 <- behavioral_data_test_set_study_2 %>%
   group_by(subject_id, word_category, category, is_word) %>%
@@
 
-behavioral_pop_out_data <- subject_level_accuracy %>%
+behavioral_pop_out_data_study_2 <- subject_level_accuracy_study_2 %>%
   filter(is_word == TRUE) %>%
@@
 
-ggplot(behavioral_pop_out_data, aes(x=`accuracy_non-category`, y=`accuracy_category`))+
+ggplot(behavioral_pop_out_data_study_2, aes(x=`accuracy_non-category`, y=`accuracy_category`))+
   geom_point()+
@@
 
-behavioral_model_moral_pop_out <- gee(correct ~ word_category,
+behavioral_model_moral_pop_out_study_2 <- gee(correct ~ word_category,
     id = subject_id,
     subset = is_word == TRUE & category == "moral",
-    data = behavioral_data_test_set,
+    data = behavioral_data_test_set_study_2,
     family = binomial,
@@
 
-coefficient_moral_pop_out <- behavioral_model_moral_pop_out$coefficients[2, 'Estimate']
-coefficient_moral_pop_out_se <- behavioral_model_moral_pop_out$coefficients[2, 'Robust S.E.']
-z_moral_pop_out <- behavioral_model_moral_pop_out$coefficients[2, 'Robust z']
-p_moral_pop_out <- (1 - pnorm(abs(z_moral_pop_out))) * 2
+coefficient_moral_pop_out_study_2 <- behavioral_model_moral_pop_out_study_2$coefficients[2, 'Estimate']
+coefficient_moral_pop_out_se_study_2 <- behavioral_model_moral_pop_out_study_2$coefficients[2, 'Robust S.E.']
+z_moral_pop_out_study_2 <- behavioral_model_moral_pop_out_study_2$coefficients[2, 'Robust z']
+p_moral_pop_out_study_2 <- (1 - pnorm(abs(z_moral_pop_out_study_2))) * 2
 
-fashion_model_moral_pop_out <- gee(correct ~ word_category,
+fashion_model_moral_pop_out_study_2 <- gee(correct ~ word_category,
     id = subject_id,
     subset = is_word == TRUE & category == "fashion",
-    data = behavioral_data_test_set,
+    data = behavioral_data_test_set_study_2,
     family = binomial,
@@
 
-coefficient_fashion_pop_out <- fashion_model_moral_pop_out$coefficients[2, 'Estimate']
-coefficient_fashion_pop_out_se <- fashion_model_moral_pop_out$coefficients[2, 'Robust S.E.']
-z_fashion_pop_out <- fashion_model_moral_pop_out$coefficients[2, 'Robust z']
-p_fashion_pop_out <- (1 - pnorm(abs(z_fashion_pop_out))) * 2
+coefficient_fashion_pop_out_study_2 <- fashion_model_moral_pop_out_study_2$coefficients[2, 'Estimate']
+coefficient_fashion_pop_out_se_study_2 <- fashion_model_moral_pop_out_study_2$coefficients[2, 'Robust S.E.']
+z_fashion_pop_out_study_2 <- fashion_model_moral_pop_out_study_2$coefficients[2, 'Robust z']
+p_fashion_pop_out_study_2 <- (1 - pnorm(abs(z_fashion_pop_out_study_2))) * 2
 
-mean_moral_in_category <- subject_level_accuracy %>%
+mean_moral_in_category_study_2 <- subject_level_accuracy_study_2 %>%
   filter(is_word == TRUE & category == "moral" & word_category == "category") %>%
@@
 
-mean_moral_out_category <- subject_level_accuracy %>%
+mean_moral_out_category_study_2 <- subject_level_accuracy_study_2 %>%
   filter(is_word == TRUE & category == "moral" & word_category == "non-category") %>%
@@
 
-mean_fashion_in_category <- subject_level_accuracy %>%
+mean_fashion_in_category_study_2 <- subject_level_accuracy_study_2 %>%
   filter(is_word == TRUE & category == "fashion" & word_category == "category") %>%
@@
 
-mean_fashion_out_category <- subject_level_accuracy %>%
+mean_fashion_out_category_study_2 <- subject_level_accuracy_study_2 %>%
   filter(is_word == TRUE & category == "fashion" & word_category == "non-category") %>%
@@
 ```
+
+In the moral condition, participants were `r mean_moral_in_category_study_2`% accurate for moral words and `r mean_moral_out_category_study_2`% accurate for non-moral words.
+This difference was not statistically significant in the GEE model, $\beta$ = `r coefficient_moral_pop_out_study_2 %>% round(3)`, *SE* = `r coefficient_moral_pop_out_se_study_2 %>% round(3)`, *z* = `r z_moral_pop_out_study_2 %>% round(3)`, *p* = `r p_moral_pop_out_study_2 %>% format(scientific=FALSE)`.
+
+In the fashion condition, participants were `r mean_fashion_in_category_study_2`% accurate for fashion words and `r mean_fashion_out_category_study_2`% accurate for non-fashion words.
+This difference was statistically significant in the GEE model, $\beta$ = `r coefficient_fashion_pop_out_study_2`, *SE* = `r coefficient_fashion_pop_out_se_study_2 %>% round(3)`, *z* = `r z_fashion_pop_out_study_2 %>% round(3)`, *p* = `r p_fashion_pop_out_study_2 %>% format(scientific=FALSE)`.
 
@@
 
-subject_eeg <- eeg_data %>%
-  filter(!subject %in% excluded_subjects) %>%
+subject_eeg_study_2 <- eeg_data_study_2 %>%
+  filter(!subject %in% excluded_subjects_study_2) %>%
   filter(electrode %in% c("Cz", "Pz")) %>%
@@
 
-grand_average <- subject_eeg %>%
+grand_average_study_2 <- subject_eeg_study_2 %>%
   group_by(t, electrode, word_category, category, is_word) %>%
@@
 
-ggplot(grand_average, aes(x=t, y=M, color=is_word, linetype=word_category)) +
+ggplot(grand_average_study_2, aes(x=t, y=M, color=is_word, linetype=word_category)) +
   geom_hline(yintercept = 0)+
@@
 
-time_window_data <- eeg_data %>%
-  filter(!subject %in% excluded_subjects) %>%
+time_window_data_study_2 <- eeg_data_study_2 %>%
+  filter(!subject %in% excluded_subjects_study_2) %>%
   filter(electrode %in% c("Cz", "Pz")) %>%
@@
 ```
+
+##### Words vs. Non-Words
+
+Following Gantman et al. (2020), we looked for word vs. non-word ERP effects at each time window at electrode Pz.
+
+```{r}
+#| label: Run GEE models for all time windows, moral data word non-word, study 2
+#| include: false
+
+p2_model_moral_word_nonword_study_2 <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "p2" & category == "moral" & electrode == "Pz",
+    data = time_window_data_study_2,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p2_model_moral_word_nonword_beta_study_2 <- p2_model_moral_word_nonword_study_2$coefficients[2, 'Estimate']
+p2_model_moral_word_nonword_se_study_2 <- p2_model_moral_word_nonword_study_2$coefficients[2, 'Robust S.E.']
+p2_model_moral_word_nonword_z_study_2 <- p2_model_moral_word_nonword_study_2$coefficients[2, 'Robust z']
+p2_model_moral_word_nonword_p_study_2 <- (1 - pnorm(abs(p2_model_moral_word_nonword_z_study_2))) * 2
+
+n2_model_moral_word_nonword_study_2 <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "n2" & category == "moral" & electrode == "Pz",
+    data = time_window_data_study_2,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+n2_model_moral_word_nonword_beta_study_2 <- n2_model_moral_word_nonword_study_2$coefficients[2, 'Estimate']
+n2_model_moral_word_nonword_se_study_2 <- n2_model_moral_word_nonword_study_2$coefficients[2, 'Robust S.E.']
+n2_model_moral_word_nonword_z_study_2 <- n2_model_moral_word_nonword_study_2$coefficients[2, 'Robust z']
+n2_model_moral_word_nonword_p_study_2 <- (1 - pnorm(abs(n2_model_moral_word_nonword_z_study_2))) * 2
+
+p3_model_moral_word_nonword_study_2 <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "p3" & category == "moral" & electrode == "Pz",
+    data = time_window_data_study_2,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p3_model_moral_word_nonword_beta_study_2 <- p3_model_moral_word_nonword_study_2$coefficients[2, 'Estimate']
+p3_model_moral_word_nonword_se_study_2 <- p3_model_moral_word_nonword_study_2$coefficients[2, 'Robust S.E.']
+p3_model_moral_word_nonword_z_study_2 <- p3_model_moral_word_nonword_study_2$coefficients[2, 'Robust z']
+p3_model_moral_word_nonword_p_study_2 <- (1 - pnorm(abs(p3_model_moral_word_nonword_z_study_2))) * 2
+
+lpp_model_moral_word_nonword_study_2 <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "lpp" & category == "moral" & electrode == "Pz",
+    data = time_window_data_study_2,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+lpp_model_moral_word_nonword_beta_study_2 <- lpp_model_moral_word_nonword_study_2$coefficients[2, 'Estimate']
+lpp_model_moral_word_nonword_se_study_2 <- lpp_model_moral_word_nonword_study_2$coefficients[2, 'Robust S.E.']
+lpp_model_moral_word_nonword_z_study_2 <- lpp_model_moral_word_nonword_study_2$coefficients[2, 'Robust z']
+lpp_model_moral_word_nonword_p_study_2 <- (1 - pnorm(abs(lpp_model_moral_word_nonword_z_study_2))) * 2
+```
+
+In the moral condition, words elicited a more positive ERP in the P2 window ($\beta$ = `r p2_model_moral_word_nonword_beta_study_2 %>% round(3)`, *SE* = `r p2_model_moral_word_nonword_se_study_2 %>% round(3)`, *z* = `r p2_model_moral_word_nonword_z_study_2 %>% round(3)`, *p* = `r p2_model_moral_word_nonword_p_study_2 %>% format(scientific=FALSE)`), N2 window ($\beta$ = `r n2_model_moral_word_nonword_beta_study_2 %>% round(3)`, *SE* = `r n2_model_moral_word_nonword_se_study_2 %>% round(3)`, *z* = `r n2_model_moral_word_nonword_z_study_2 %>% round(3)`, *p* = `r n2_model_moral_word_nonword_p_study_2 %>% format(scientific=FALSE)`), and P3 window ($\beta$ = `r p3_model_moral_word_nonword_beta_study_2 %>% round(3)`, *SE* = `r p3_model_moral_word_nonword_se_study_2 %>% round(3)`, *z* = `r p3_model_moral_word_nonword_z_study_2 %>% round(3)`, *p* = `r p3_model_moral_word_nonword_p_study_2 %>% format(scientific=FALSE)`).
+There was no significant effect in the LPP window ($\beta$ = `r lpp_model_moral_word_nonword_beta_study_2 %>% round(3)`, *SE* = `r lpp_model_moral_word_nonword_se_study_2 %>% round(3)`, *z* = `r lpp_model_moral_word_nonword_z_study_2 %>% round(3)`, *p* = `r lpp_model_moral_word_nonword_p_study_2 %>% format(scientific=FALSE)`).
+
+```{r}
+#| label: Run GEE models for all time windows, fashion data word non-word, study 2
+#| include: false
+
+p2_model_fashion_word_nonword_study_2 <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "p2" & category == "fashion" & electrode == "Pz",
+    data = time_window_data_study_2,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p2_model_fashion_word_nonword_beta_study_2 <- p2_model_fashion_word_nonword_study_2$coefficients[2, 'Estimate']
+p2_model_fashion_word_nonword_se_study_2 <- p2_model_fashion_word_nonword_study_2$coefficients[2, 'Robust S.E.']
+p2_model_fashion_word_nonword_z_study_2 <- p2_model_fashion_word_nonword_study_2$coefficients[2, 'Robust z']
+p2_model_fashion_word_nonword_p_study_2 <- (1 - pnorm(abs(p2_model_fashion_word_nonword_z_study_2))) * 2
+
+n2_model_fashion_word_nonword_study_2 <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "n2" & category == "fashion" & electrode == "Pz",
+    data = time_window_data_study_2,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+n2_model_fashion_word_nonword_beta_study_2 <- n2_model_fashion_word_nonword_study_2$coefficients[2, 'Estimate']
+n2_model_fashion_word_nonword_se_study_2 <- n2_model_fashion_word_nonword_study_2$coefficients[2, 'Robust S.E.']
+n2_model_fashion_word_nonword_z_study_2 <- n2_model_fashion_word_nonword_study_2$coefficients[2, 'Robust z']
+n2_model_fashion_word_nonword_p_study_2 <- (1 - pnorm(abs(n2_model_fashion_word_nonword_z_study_2))) * 2
+
+p3_model_fashion_word_nonword_study_2 <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "p3" & category == "fashion" & electrode == "Pz",
+    data = time_window_data_study_2,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p3_model_fashion_word_nonword_beta_study_2 <- p3_model_fashion_word_nonword_study_2$coefficients[2, 'Estimate']
+p3_model_fashion_word_nonword_se_study_2 <- p3_model_fashion_word_nonword_study_2$coefficients[2, 'Robust S.E.']
+p3_model_fashion_word_nonword_z_study_2 <- p3_model_fashion_word_nonword_study_2$coefficients[2, 'Robust z']
+p3_model_fashion_word_nonword_p_study_2 <- (1 - pnorm(abs(p3_model_fashion_word_nonword_z_study_2))) * 2
+
+lpp_model_fashion_word_nonword_study_2 <- gee(v ~ is_word,
+    id = subject,
+    subset = erp_component == "lpp" & category == "fashion" & electrode == "Pz",
+    data = time_window_data_study_2,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+lpp_model_fashion_word_nonword_beta_study_2 <- lpp_model_fashion_word_nonword_study_2$coefficients[2, 'Estimate']
+lpp_model_fashion_word_nonword_se_study_2 <- lpp_model_fashion_word_nonword_study_2$coefficients[2, 'Robust S.E.']
+lpp_model_fashion_word_nonword_z_study_2 <- lpp_model_fashion_word_nonword_study_2$coefficients[2, 'Robust z']
+lpp_model_fashion_word_nonword_p_study_2 <- (1 - pnorm(abs(lpp_model_fashion_word_nonword_z_study_2))) * 2
+
+```
+
+In the fashion condition, there was no significant difference in any of the time windows; P2 window ($\beta$ = `r p2_model_fashion_word_nonword_beta_study_2 %>% round(3)`, *SE* = `r p2_model_fashion_word_nonword_se_study_2 %>% round(3)`, *z* = `r p2_model_fashion_word_nonword_z_study_2 %>% round(3)`, *p* = `r p2_model_fashion_word_nonword_p_study_2 %>% format(scientific=FALSE)`), N2 window ($\beta$ = `r n2_model_fashion_word_nonword_beta_study_2 %>% round(3)`, *SE* = `r n2_model_fashion_word_nonword_se_study_2 %>% round(3)`, *z* = `r n2_model_fashion_word_nonword_z_study_2 %>% round(3)`, *p* = `r n2_model_fashion_word_nonword_p_study_2 %>% format(scientific=FALSE)`), P3 window ($\beta$ = `r p3_model_fashion_word_nonword_beta_study_2 %>% round(3)`, *SE* = `r p3_model_fashion_word_nonword_se_study_2 %>% round(3)`, *z* = `r p3_model_fashion_word_nonword_z_study_2 %>% round(3)`, *p* = `r p3_model_fashion_word_nonword_p_study_2 %>% format(scientific=FALSE)`), and LPP window ($\beta$ = `r lpp_model_fashion_word_nonword_beta_study_2 %>% round(3)`, *SE* = `r lpp_model_fashion_word_nonword_se_study_2 %>% round(3)`, *z* = `r lpp_model_fashion_word_nonword_z_study_2 %>% round(3)`, *p* = `r lpp_model_fashion_word_nonword_p_study_2 %>% format(scientific=FALSE)`).
+
+##### Pop-out effects
+
+Also following Gantman et al. (2020), we looked for ERP differences related to the category vs. non-category distinction in all four time windows at electrode Cz.
+
+```{r}
+#| label: Run GEE models for all time windows, moral data pop-out, study 2
+#| include: false
+
+p2_model_moral_popout_study_2 <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "p2" & category == "moral" & is_word == TRUE & electrode == "Cz",
+    data = time_window_data_study_2,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p2_model_moral_popout_beta_study_2 <- p2_model_moral_popout_study_2$coefficients[2, 'Estimate']
+p2_model_moral_popout_se_study_2 <- p2_model_moral_popout_study_2$coefficients[2, 'Robust S.E.']
+p2_model_moral_popout_z_study_2 <- p2_model_moral_popout_study_2$coefficients[2, 'Robust z']
+p2_model_moral_popout_p_study_2 <- (1 - pnorm(abs(p2_model_moral_popout_z_study_2))) * 2
+
+n2_model_moral_popout_study_2 <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "n2" & category == "moral" & is_word == TRUE & electrode == "Cz",
+    data = time_window_data_study_2,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+n2_model_moral_popout_beta_study_2 <- n2_model_moral_popout_study_2$coefficients[2, 'Estimate']
+n2_model_moral_popout_se_study_2 <- n2_model_moral_popout_study_2$coefficients[2, 'Robust S.E.']
+n2_model_moral_popout_z_study_2 <- n2_model_moral_popout_study_2$coefficients[2, 'Robust z']
+n2_model_moral_popout_p_study_2 <- (1 - pnorm(abs(n2_model_moral_popout_z_study_2))) * 2
+
+p3_model_moral_popout_study_2 <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "p3" & category == "moral"& is_word == TRUE & electrode == "Cz",
+    data = time_window_data_study_2,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p3_model_moral_popout_beta_study_2 <- p3_model_moral_popout_study_2$coefficients[2, 'Estimate']
+p3_model_moral_popout_se_study_2 <- p3_model_moral_popout_study_2$coefficients[2, 'Robust S.E.']
+p3_model_moral_popout_z_study_2 <- p3_model_moral_popout_study_2$coefficients[2, 'Robust z']
+p3_model_moral_popout_p_study_2 <- (1 - pnorm(abs(p3_model_moral_popout_z_study_2))) * 2
+
+lpp_model_moral_popout_study_2 <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "lpp" & category == "moral"& is_word == TRUE & electrode == "Cz",
+    data = time_window_data_study_2,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+lpp_model_moral_popout_beta_study_2 <- lpp_model_moral_popout_study_2$coefficients[2, 'Estimate']
+lpp_model_moral_popout_se_study_2 <- lpp_model_moral_popout_study_2$coefficients[2, 'Robust S.E.']
+lpp_model_moral_popout_z_study_2 <- lpp_model_moral_popout_study_2$coefficients[2, 'Robust z']
+lpp_model_moral_popout_p_study_2 <- (1 - pnorm(abs(lpp_model_moral_popout_z_study_2))) * 2
+
+```
+
+In the moral condition, there was a significant difference between moral and non-moral words in the P2 window ($\beta$ = `r p2_model_moral_popout_beta_study_2 %>% round(3)`, *SE* = `r p2_model_moral_popout_se_study_2 %>% round(3)`, *z* = `r p2_model_moral_popout_z_study_2 %>% round(3)`, *p* = `r p2_model_moral_popout_p_study_2 %>% format(scientific=FALSE)`), but this difference was in the opposite direction predicted by Gantman et al.
+(2020).
+There were no significant differences between moral and non-moral words in the N2 window ($\beta$ = `r n2_model_moral_popout_beta_study_2 %>% round(3)`, *SE* = `r n2_model_moral_popout_se_study_2 %>% round(3)`, *z* = `r n2_model_moral_popout_z_study_2 %>% round(3)`, *p* = `r n2_model_moral_popout_p_study_2 %>% format(scientific=FALSE)`), P3 window ($\beta$ = `r p3_model_moral_popout_beta_study_2 %>% round(3)`, *SE* = `r p3_model_moral_popout_se_study_2 %>% round(3)`, *z* = `r p3_model_moral_popout_z_study_2 %>% round(3)`, *p* = `r p3_model_moral_popout_p_study_2 %>% format(scientific=FALSE)`), and the LPP window ($\beta$ = `r lpp_model_moral_popout_beta_study_2 %>% round(3)`, *SE* = `r lpp_model_moral_popout_se_study_2 %>% round(3)`, *z* = `r lpp_model_moral_popout_z_study_2 %>% round(3)`, *p* = `r lpp_model_moral_popout_p_study_2 %>% format(scientific=FALSE)`).
+
+```{r}
+#| label: Run GEE models for all time windows, fashion data pop-out, study 2
+#| include: false
+
+p2_model_fashion_popout_study_2 <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "p2" & category == "fashion" & is_word == TRUE & electrode == "Cz",
+    data = time_window_data_study_2,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p2_model_fashion_popout_beta_study_2 <- p2_model_fashion_popout_study_2$coefficients[2, 'Estimate']
+p2_model_fashion_popout_se_study_2 <- p2_model_fashion_popout_study_2$coefficients[2, 'Robust S.E.']
+p2_model_fashion_popout_z_study_2 <- p2_model_fashion_popout_study_2$coefficients[2, 'Robust z']
+p2_model_fashion_popout_p_study_2 <- (1 - pnorm(abs(p2_model_fashion_popout_z_study_2))) * 2
+
+n2_model_fashion_popout_study_2 <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "n2" & category == "fashion"& is_word == TRUE & electrode == "Cz",
+    data = time_window_data_study_2,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+n2_model_fashion_popout_beta_study_2 <- n2_model_fashion_popout_study_2$coefficients[2, 'Estimate']
+n2_model_fashion_popout_se_study_2 <- n2_model_fashion_popout_study_2$coefficients[2, 'Robust S.E.']
+n2_model_fashion_popout_z_study_2 <- n2_model_fashion_popout_study_2$coefficients[2, 'Robust z']
+n2_model_fashion_popout_p_study_2 <- (1 - pnorm(abs(n2_model_fashion_popout_z_study_2))) * 2
+
+p3_model_fashion_popout_study_2 <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "p3" & category == "fashion"& is_word == TRUE & electrode == "Cz",
+    data = time_window_data_study_2,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+p3_model_fashion_popout_beta_study_2 <- p3_model_fashion_popout_study_2$coefficients[2, 'Estimate']
+p3_model_fashion_popout_se_study_2 <- p3_model_fashion_popout_study_2$coefficients[2, 'Robust S.E.']
+p3_model_fashion_popout_z_study_2 <- p3_model_fashion_popout_study_2$coefficients[2, 'Robust z']
+p3_model_fashion_popout_p_study_2 <- (1 - pnorm(abs(p3_model_fashion_popout_z_study_2))) * 2
+
+lpp_model_fashion_popout_study_2 <- gee(v ~ word_category,
+    id = subject,
+    subset = erp_component == "lpp" & category == "fashion"& is_word == TRUE & electrode == "Cz",
+    data = time_window_data_study_2,
+    family = gaussian,
+    corstr = "exchangeable") %>% summary()
+
+lpp_model_fashion_popout_beta_study_2 <- lpp_model_fashion_popout_study_2$coefficients[2, 'Estimate']
+lpp_model_fashion_popout_se_study_2 <- lpp_model_fashion_popout_study_2$coefficients[2, 'Robust S.E.']
+lpp_model_fashion_popout_z_study_2 <- lpp_model_fashion_popout_study_2$coefficients[2, 'Robust z']
+lpp_model_fashion_popout_p_study_2 <- (1 - pnorm(abs(lpp_model_fashion_popout_z_study_2))) * 2
+
+```
+
+In the fashion condition, there fashion words elicited a more positive ERP than non-fashion words in the P3 window ($\beta$ = `r p3_model_fashion_popout_beta_study_2 %>% round(3)`, *SE* = `r p3_model_fashion_popout_se_study_2 %>% round(3)`, *z* = `r p3_model_fashion_popout_z_study_2 %>% round(3)`, *p* = `r p3_model_fashion_popout_p_study_2 %>% format(scientific=FALSE)`) and LPP window ($\beta$ = `r lpp_model_fashion_popout_beta_study_2 %>% round(3)`, *SE* = `r lpp_model_fashion_popout_se_study_2 %>% round(3)`, *z* = `r lpp_model_fashion_popout_z_study_2 %>% round(3)`, *p* = `r lpp_model_fashion_popout_p_study_2 %>% format(scientific=FALSE)`).
+There was no significant difference in the P2 window ($\beta$ = `r p2_model_fashion_popout_beta_study_2 %>% round(3)`, *SE* = `r p2_model_fashion_popout_se_study_2 %>% round(3)`, *z* = `r p2_model_fashion_popout_z_study_2 %>% round(3)`, *p* = `r p2_model_fashion_popout_p_study_2 %>% format(scientific=FALSE)`) and N2 window ($\beta$ = `r n2_model_fashion_popout_beta_study_2 %>% round(3)`, *SE* = `r n2_model_fashion_popout_se_study_2 %>% round(3)`, *z* = `r n2_model_fashion_popout_z_study_2 %>% round(3)`, *p* = `r n2_model_fashion_popout_p_study_2 %>% format(scientific=FALSE)`).
